\newpage
\phantomsection
\label{prf:faa-di-bruno}
\LRAProofFor{thm:faa-di-bruno}

\begin{remark*}[Return]
\hyperref[thm:faa-di-bruno]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Faa di Bruno's Formula]
Under the hypotheses of \hyperref[thm:faa-di-bruno]{Faa di Bruno's Formula},
\[
  \frac{d^n}{dx^n}f(g(x))
  =
  \sum_{\sum_{m=1}^{n}mk_m=n}
  \frac{n!}{\prod_{m=1}^{n}k_m!\,(m!)^{k_m}}\,
  f^{(k)}(g(x))
  \prod_{m=1}^{n}\bigl(g^{(m)}(x)\bigr)^{k_m},
\]
where \(k=\sum_{m=1}^{n}k_m\).
\end{theorem*}

\begin{proof}[Professional Standard Proof]
\LRAProofBodyStart
The proof is by induction on \(n\). At \(n=1\), the only tuple is
\(k_1=1\), so the formula reads
\[
  (f\circ g)'=f'(g)g',
\]
which is the chain rule.

Assume the formula holds at order \(n\). Differentiate one summand
\[
  C_{\mathbf{k}}\,f^{(k)}(g)\prod_{m=1}^{n}\bigl(g^{(m)}\bigr)^{k_m},
  \qquad
  C_{\mathbf{k}}=\frac{n!}{\prod_{m=1}^{n}k_m!\,(m!)^{k_m}}.
\]
There are two types of contributions. A derivative may hit
\(f^{(k)}(g)\); by the chain rule this creates
\(f^{(k+1)}(g)g'\), which adds one block of size \(1\). Or a derivative may
hit one of the \(k_m\) factors \(g^{(m)}\); by the product rule this raises
one block of size \(m\) to a block of size \(m+1\), with multiplicity
\(k_m\).

Thus differentiating the order-\(n\) partition sum produces exactly the
tuples \(\mathbf{j}=(j_1,\ldots,j_{n+1})\) satisfying
\(\sum m j_m=n+1\). Conversely, each such tuple arises uniquely from one of
these two inverse moves: either remove one size-\(1\) block, or lower one
block of size \(m+1\) to size \(m\). The coefficient attached to a fixed
\(\mathbf{j}\) is therefore the sum of the contributions of all inverse
moves. The elementary factorial simplification is precisely the recurrence
for the number of set partitions with block multiplicities \(\mathbf{j}\):
\[
  \frac{(n+1)!}{\prod_{m=1}^{n+1}j_m!\,(m!)^{j_m}}.
\]
This is the desired coefficient at order \(n+1\), completing the induction.
\end{proof}

\begin{proof}[Detailed Learning Proof]
\LRAProofBodyStart
The tuple \((k_1,\ldots,k_n)\) records how the \(n\) differentiations have
been grouped. A block of size \(m\) means that \(m\) differentiations have
combined to produce a factor \(g^{(m)}\). The number \(k=\sum k_m\) counts
how many blocks there are, so the outside function has been differentiated
\(k\) times.

When differentiating once more, there are only two possible events. The new
derivative may start a new size-\(1\) block by hitting the outer factor
\(f^{(k)}(g)\), or it may enlarge an existing block by hitting one of the
inner factors \(g^{(m)}\). The factorial coefficient keeps track of how many
ways the same block-size pattern can occur: \(m!\) removes order inside a
block, and \(k_m!\) removes order among equal-size blocks.

The cleaner proof, once Taylor expansions are available, is to compose the
Taylor series of \(f\) and \(g\) and read off the coefficient of the
\(n\)-th power. That proof explains the same partition sum as coefficient
collection by total inner degree.
\end{proof}

\begin{remark*}[Proof structure]
Induct on order. The inductive step differentiates the partition sum and
re-indexes the resulting terms by the partitions of \(n+1\).
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[thm:chain-rule]{Theorem: Chain Rule}
  \item \hyperref[thm:leibniz-rule]{Theorem: Leibniz Rule}
  \item \hyperref[def:higher-derivatives]{Definition: Higher Derivatives}
\end{itemize}
\end{dependencies}

\clearpage
