\newpage
\phantomsection
\label{prf:monotone-darboux-integrable}
\LRAProofFor{thm:monotone-darboux-integrable}
\begin{remark*}[Return]\hyperref[thm:monotone-darboux-integrable]{Return to Theorem}\end{remark*}
\begin{theorem*}[Monotone Functions Are Darboux-Integrable]
Every monotone function \(f:[a,b]\to\mathbb R\) is Darboux-integrable.
\end{theorem*}
\begin{proof}[Professional Standard Proof]
\LRAProofBodyStart
Assume first that \(f\) is increasing. Let \(\varepsilon>0\). If
\(f(b)=f(a)\), then \(f\) is constant and the result is immediate. Otherwise,
choose a partition \(P=\{a=x_0<\cdots<x_n=b\}\) with mesh
\[
  \|P\|<\frac{\varepsilon}{f(b)-f(a)}.
\]
For an increasing function on \([x_{i-1},x_i]\),
\[
  m_i=f(x_{i-1}),\qquad M_i=f(x_i),
\]
so
\[
  U(f,P)-L(f,P)
  =
  \sum_{i=1}^n\bigl(f(x_i)-f(x_{i-1})\bigr)\Delta x_i.
\]
Since every \(\Delta x_i\le \|P\|\),
\[
  U(f,P)-L(f,P)
  \le
  \|P\|\sum_{i=1}^n\bigl(f(x_i)-f(x_{i-1})\bigr)
  =
  \|P\|\,(f(b)-f(a))
  <\varepsilon.
\]
By the Darboux criterion, \(f\) is integrable.

If \(f\) is decreasing, apply the increasing case to \(-f\). Since
integrability is preserved by scalar multiplication, \(f\) is Darboux-integrable.
\end{proof}
\begin{proof}[Detailed Learning Proof]
\LRAProofBodyStart
The key point is that a monotone function cannot oscillate back and forth.
On each small interval the largest possible vertical error is the change from
the left endpoint to the right endpoint. When those vertical changes are
summed over the partition, all intermediate terms cancel: the total vertical
movement is only \(f(b)-f(a)\). Multiplying by the largest slab width gives a
bound for the whole Darboux gap. Refining the mesh makes that product as small
as desired.
\end{proof}
\begin{remark*}[Proof structure]
For increasing functions, bound the Darboux gap by mesh times total vertical
variation. Reduce decreasing functions by negation.
\end{remark*}
\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:darboux-sums]{Lower and Upper Darboux Sums}.
  \item \hyperref[thm:darboux-criterion]{Darboux Criterion}.
\end{itemize}
\end{dependencies}
\clearpage
