% ============================================================
%  \S{}0  Foundational Analysis Properties
%  volume-iii/book-analysis-i/real-analysis/notes/proof-techniques/
%  proof-patterns-and-algorithms.tex
% ============================================================

\subsection{Foundational Analysis Properties}
\label{sec:foundational-analysis-properties}

\begingroup
\sloppy
\emergencystretch=3em

\begin{toolkitbox}{Foundational Analysis Properties --- Quick Reference}
\small
\begin{tabular}{p{0.22\linewidth} p{0.25\linewidth} p{0.43\linewidth}}
\toprule
\textbf{Concept} & \textbf{Goal} & \textbf{Proof mechanism / logical form} \\
\midrule
Well-definedness
  & Consistency
  & $x\sim y \Rightarrow F(x)=F(y)$ \\
Existence
  & Feasibility
  & $\exists x\;P(x)$ \\
Uniqueness
  & Singularity
  & $P(x_1)\land P(x_2)\Rightarrow x_1=x_2$ \\
Linearity
  & Decomposition
  & $L(f+g)=L(f)+L(g)$ and $L(cf)=cL(f)$ \\
Uniformity
  & One choice works globally
  & $\forall\varepsilon>0,\exists\delta>0,\forall x,y,\;Q(\varepsilon,\delta,x,y)$ \\
Equivalence
  & Interchangeable descriptions
  & $A\Rightarrow B$ and $B\Rightarrow A$ \\
Characterisation
  & Usable test
  & $P(x)\Longleftrightarrow C(x)$ \\
Estimate
  & Control
  & $A\leq B$, $|A|<\varepsilon$, or $d(A,B)<\varepsilon$ \\
Boundedness
  & Two-sided control
  & $\exists l,u\in S\;\forall x\in A\;(l\leq x\leq u)$ \\
Upper/lower control
  & One-sided domination
  & $\forall x\in A\;(x\leq u)$ or $\forall x\in A\;(l\leq x)$ \\
Extremality
  & Realized optimality
  & $m\in A\land \operatorname{Bound}(m,A)$ \\
Least/greatest character
  & Optimal bound
  & $\operatorname{Bound}(b,A)\land \forall c\,(\operatorname{Bound}(c,A)\Rightarrow b\preceq c)$ \\
Monotonicity
  & Order preservation
  & Start with $x\leq y$ and prove $f(x)\leq f(y)$, or the reverse \\
Closure
  & Staying inside a class
  & $P(x)\land P(y)\Rightarrow P(x\star y)$ \\
Approximation
  & Arbitrary precision
  & $\forall\varepsilon>0\;\exists x\;d(x,a)<\varepsilon$ \\
\bottomrule
\end{tabular}
\end{toolkitbox}

Many proofs in analysis are not isolated inventions. They prove recurring
structural properties: a definition is independent of choices, an object
exists, there is only one possible object, an operation respects addition and
scalars, a single parameter works everywhere, or two definitions describe the
same phenomenon. Naming the property first tells us what the proof must do.

\subsection*{Well-Definedness}
\label{subsec:property-well-definedness}

Well-definedness appears whenever an object is defined using choices:
representatives of equivalence classes, selected sequences, selected
partitions, or selected approximations. The goal is to prove that different
allowed choices give the same output.
\[
  x\sim x' \Rightarrow F(x)=F(x').
\]

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Identify the choice built into the definition.
  \item Take two allowed choices, usually $x$ and $x'$ with $x\sim x'$.
  \item Compute or compare the two proposed outputs.
  \item Show the outputs agree in the codomain.
\end{enumerate}
\end{remark}

\begin{remark}[Crucial logic]
The output must be independent of the chosen representative. If changing the
representative changes the output, the proposed definition is not a function
on the quotient or chosen domain.
\end{remark}

\subsection*{Existence}
\label{subsec:property-existence}

Existence proves that at least one object satisfying a property is available:
\[
  \exists x\;P(x).
\]
In analysis the object might be a limit, a supremum, a point in an interval,
a subsequence, a bound, an index $N$, a radius $\delta$, or a partition.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Determine every requirement in the property $P$.
  \item Produce a candidate explicitly, or invoke a theorem that guarantees
        one.
  \item Verify the candidate belongs to the required domain.
  \item Verify the candidate satisfies every part of $P$.
\end{enumerate}
\end{remark}

\begin{remark}[Constructive and nonconstructive existence]
A constructive proof names the object directly. A nonconstructive proof uses
a theorem such as completeness, the intermediate value theorem, or
Bolzano--Weierstrass. In both cases, the final burden is the same: the object
must satisfy the stated property.
\end{remark}

\subsection*{Uniqueness}
\label{subsec:property-uniqueness}

Uniqueness proves that at most one object can satisfy a property:
\[
  P(x_1)\land P(x_2)\Rightarrow x_1=x_2.
\]
It does not by itself prove existence. It only proves that two successful
candidates cannot be distinct.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Assume $x_1$ and $x_2$ both satisfy $P$.
  \item Use the defining property of $x_1$ and the defining property of $x_2$.
  \item Derive two-sided comparison, zero distance, or identical defining
        data.
  \item Conclude $x_1=x_2$.
\end{enumerate}
\end{remark}

\begin{remark}[Common analysis forms]
For suprema, show $s\leq t$ and $t\leq s$. For limits, show
$|L-M|<\varepsilon$ for every $\varepsilon>0$, hence $L=M$. In metric spaces,
show $d(x_1,x_2)=0$.
\end{remark}

\subsection*{Linearity}
\label{subsec:property-linearity}

Linearity proves that an operation decomposes over addition and scalar
multiplication:
\[
  L(f+g)=L(f)+L(g),
  \qquad
  L(cf)=cL(f).
\]
The goal is not merely algebraic neatness. Linearity says that a complicated
input can be analysed by splitting it into simpler pieces.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Take arbitrary admissible inputs $f,g$ and scalar $c$.
  \item Expand $L(f+g)$ using the definition of $L$ and the definition of
        addition.
  \item Rearrange the expression until $L(f)+L(g)$ appears.
  \item Repeat with $L(cf)$ and show it equals $cL(f)$.
\end{enumerate}
\end{remark}

\begin{remark}[Typical analysis examples]
Limits, derivatives, integrals, and many summation operators have linearity
theorems. Each proof follows the same shape: expand the left side, split the
expression, and identify the two pieces.
\end{remark}

\subsection*{Uniformity}
\label{subsec:property-uniformity}

Uniformity means that one choice works for all relevant points at once. The
prototype is not just uniform continuity, but any statement where a witness is
chosen before the point is allowed to vary:
\[
  \forall\varepsilon>0,\;\exists\delta>0,\;\forall x,y,\;Q(\varepsilon,\delta,x,y).
\]
The key phrase is ``one choice.'' The same $N$, $\delta$, bound, or partition
must work globally over the specified domain.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Fix the tolerance or target requirement.
  \item Choose a single witness that depends only on the allowed global data.
  \item Let the point, pair of points, function, or index vary arbitrarily.
  \item Verify that the same witness works in every permitted case.
\end{enumerate}
\end{remark}

\begin{remark}[Contrast with pointwise statements]
Pointwise statements allow the witness to depend on the point. Uniform
statements do not. The order of quantifiers is the whole issue:
\[
  \forall x\,\exists\delta
  \quad\text{is pointwise, while}\quad
  \exists\delta\,\forall x
  \quad\text{is uniform.}
\]
\end{remark}

\subsection*{Equivalence}
\label{subsec:property-equivalence}

Equivalence proves that two statements are logically interchangeable:
\[
  A\Longleftrightarrow B.
\]
Such theorems are common because analysis often has several descriptions of
the same phenomenon: epsilon-delta, sequential, order-theoretic, topological,
or integral.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Prove $A\Rightarrow B$.
  \item Prove $B\Rightarrow A$.
  \item Keep the assumptions for the two directions separate.
  \item After both directions are proved, either description may be used.
\end{enumerate}
\end{remark}

\begin{remark}[Typical analysis examples]
Sequential and epsilon-delta definitions of continuity are equivalent.
Riemann and Darboux integrability are equivalent under the appropriate
hypotheses. A set is closed exactly when it contains the limits of all
convergent sequences from the set.
\end{remark}

\subsection*{Characterisation}
\label{subsec:property-characterisation}

A characterisation is an equivalence whose purpose is to turn a definition
into a usable test:
\[
  P(x)\Longleftrightarrow C(x).
\]
The theorem does not merely say two statements agree. It supplies a criterion
that can be used in later proofs.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Identify the original definition.
  \item Identify the proposed criterion.
  \item Prove definition $\Rightarrow$ criterion.
  \item Prove criterion $\Rightarrow$ definition.
\end{enumerate}
\end{remark}

\begin{remark}[Typical analysis examples]
The epsilon characterisation of the supremum turns least-upper-bound language
into an approximation rule. Cauchy criteria turn convergence questions into
internal distance estimates. Sequential criteria turn topological conditions
into statements about sequences.
\end{remark}

\subsection*{Estimates and Bounds}
\label{subsec:property-estimates}

An estimate proves control:
\[
  A\leq B,\qquad |A|<\varepsilon,\qquad d(A,B)<\varepsilon.
\]
The aim is not to compute the exact value. The aim is to put the target
quantity inside a range that is strong enough for the theorem.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Identify the quantity that must be controlled.
  \item Replace it by a larger or simpler quantity using valid inequalities.
  \item Use hypotheses to replace variable terms by constants or small
        errors.
  \item End with the required bound.
\end{enumerate}
\end{remark}

\begin{remark}[Typical analysis examples]
Showing a sequence is bounded, proving an error term tends to zero, bounding
a Riemann-sum error, or proving $|f(x)-L|<\varepsilon$ are all estimate
problems. The proof is a chain of control.
\end{remark}

\subsection*{Boundedness}
\label{subsec:property-boundedness}

Boundedness proves two-sided control. In an ordered setting, the usual form is
that a set or sequence is bounded above and bounded below:
\[
  \exists l,u\in S\;\forall x\in A\;(l\leq x\leq u).
\]

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Prove bounded above by finding a candidate upper bound.
  \item Prove bounded below by finding a candidate lower bound.
  \item Verify both candidates work for every element under consideration.
  \item Conclude that the object is bounded.
\end{enumerate}
\end{remark}

\subsection*{Upper and Lower Control}
\label{subsec:property-upper-lower-control}

Upper and lower control prove one-sided domination. The proof focuses on a
candidate bound and checks that every element lies on the required side of it:
\[
  \forall x\in A\;(x\leq u),
  \qquad
  \forall x\in A\;(l\leq x).
\]

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Name the candidate upper or lower bound.
  \item Let an arbitrary element of the set be given.
  \item Use the hypotheses or definition of the set to compare that element
        with the candidate.
  \item Since the element was arbitrary, conclude the one-sided bound.
\end{enumerate}
\end{remark}

\subsection*{Extremality}
\label{subsec:property-extremality}

Extremality proves that an optimal value is actually realized by the object
being studied. A maximum is not merely an upper bound; it is an upper bound
that belongs to the set. A minimum is the corresponding realized lower bound.
\[
  \operatorname{Maximum}(m,A)
  \Longleftrightarrow
  (m\in A)\land \operatorname{UpperBound}(m,A),
\]
\[
  \operatorname{Minimum}(m,A)
  \Longleftrightarrow
  (m\in A)\land \operatorname{LowerBound}(m,A).
\]

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Prove the candidate belongs to the set.
  \item Prove the candidate is the appropriate one-sided bound.
  \item Combine membership with the bound condition.
  \item Conclude maximum or minimum.
\end{enumerate}
\end{remark}

\subsection*{Least and Greatest Character}
\label{subsec:property-least-greatest-character}

Least and greatest character proves optimality among competitors. For a
supremum, the candidate must first be an upper bound, and then it must be no
larger than every other upper bound. Infimum proofs reverse the direction.
\[
  \operatorname{Supremum}(s,A)
  \Longleftrightarrow
  \operatorname{UpperBound}(s,A)
  \land
  \forall u\in S\,
  \bigl(\operatorname{UpperBound}(u,A)\Rightarrow s\leq u\bigr),
\]
\[
  \operatorname{Infimum}(i,A)
  \Longleftrightarrow
  \operatorname{LowerBound}(i,A)
  \land
  \forall l\in S\,
  \bigl(\operatorname{LowerBound}(l,A)\Rightarrow l\leq i\bigr).
\]

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Prove the candidate is a bound of the required kind.
  \item Let an arbitrary competing bound be given.
  \item Compare the candidate with that competing bound.
  \item Conclude the candidate is the least upper bound or greatest lower
        bound.
\end{enumerate}
\end{remark}

\subsection*{Monotonicity}
\label{subsec:property-monotonicity}

Monotonicity proves order preservation or order reversal:
\[
  x\leq y \Rightarrow f(x)\leq f(y),
  \qquad
  x\leq y \Rightarrow f(y)\leq f(x).
\]
The proof begins with an arbitrary ordered pair and carries that order through
the definitions.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Take arbitrary points $x$ and $y$ with $x\leq y$.
  \item Expand the definitions of the function or operation.
  \item Use order rules and hypotheses to compare the outputs.
  \item Conclude that the order is preserved or reversed.
\end{enumerate}
\end{remark}

\subsection*{Closure}
\label{subsec:property-closure}

Closure proves that a class is stable under an operation. One starts with
objects already known to belong to the class, combines them, and then verifies
that the result still satisfies the defining property.
\[
  P(x)\land P(y)\Rightarrow P(x\star y).
\]
For closure under scalar operations, the same pattern becomes
\[
  P(x)\Rightarrow P(c\star x)
\]
for every admissible scalar or parameter $c$.

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Take arbitrary objects from the class.
  \item Form the object produced by the operation.
  \item Check every condition in the definition of the class.
  \item Conclude the result remains inside the class.
\end{enumerate}
\end{remark}

\subsection*{Approximation}
\label{subsec:property-approximation}

Approximation proves arbitrary precision. The proof usually begins with a
tolerance and constructs an object close enough to a target:
\[
  \forall\varepsilon>0\;\exists x\;d(x,a)<\varepsilon.
\]

\begin{remark}[Proof sketch]
\begin{enumerate}
  \item Fix an arbitrary tolerance $\varepsilon>0$.
  \item Choose or construct an approximating object.
  \item Estimate the error between the approximation and the target.
  \item Show the error is below $\varepsilon$.
\end{enumerate}
\end{remark}

\subsection*{A Classification Pass}
\label{subsec:property-classification-pass}

Before proving a theorem, classify its job:
\begin{itemize}
  \item Does the statement depend on choices? Check well-definedness.
  \item Does it ask for an object? Prove existence.
  \item Does it say only one object can work? Prove uniqueness.
  \item Does it say an operation splits across sums and scalars? Prove
        linearity.
  \item Does one witness have to work for every point? Prove uniformity.
  \item Does it say two descriptions agree? Prove equivalence.
  \item Does it give a test for a definition? Prove a characterisation.
  \item Does it ask for smallness or control? Prove an estimate.
  \item Does it ask for two-sided order control? Prove boundedness.
  \item Does it ask for one-sided order control? Prove an upper or lower
        bound.
  \item Does it ask for a realized best element? Prove extremality.
  \item Does it ask for the best bound among all bounds? Prove least or
        greatest character.
  \item Does it preserve or reverse order? Prove monotonicity.
  \item Does it stay inside a class after an operation? Prove closure.
  \item Does it ask for arbitrary precision? Prove approximation.
\end{itemize}

\begin{remark}[The point]
The classification does not solve the proof, but it tells us what a completed
proof must contain. For example, an existence proof must exhibit or obtain an
object, while a uniqueness proof must compare two candidates. An equivalence
proof must have two directions, while a uniformity proof must choose one
witness before the arbitrary point is fixed.
\end{remark}

\endgroup
