\subsection*{Where This Sits}

\begin{exposition}
McShane is the gauge integral that looks almost indistinguishable from
Henstock--Kurzweil until one notices where the tags are allowed to live. HK
keeps each tag inside its own slab. McShane lets a tag control a slab from
outside it, as long as the slab lies inside the tag's gauge ball.
\end{exposition}

\begin{remark*}[Interpretation]
Henstock--Kurzweil says:
\[
  \xi_i\in[x_{i-1},x_i]
  \quad\text{and}\quad
  [x_{i-1},x_i]\subset
  (\xi_i-\delta(\xi_i),\xi_i+\delta(\xi_i)).
\]
McShane drops only the first requirement. The interval still has to be locally
small around its tag, but the tag need not lie in the interval it controls.
That small freedom is decisive: it prevents the conditional cancellation that
lets HK integrate every derivative.
\end{remark*}

\begin{remark*}[Interpretation]
\[
\begin{array}{c|c|c|c}
\text{Integral} & \text{Gauge} & \text{Tag position} & \text{Class on }[a,b]\\
\hline
\text{Henstock--Kurzweil} & \delta(x) & \xi_i\in I_i &
\mathcal{HK}\\
\text{McShane} & \delta(x) & \xi_i\in[a,b]\text{ and }I_i\subset B(\xi_i,\delta(\xi_i)) &
\mathcal L
\end{array}
\]
Both use a variable gauge. The difference is not the step-size field; it is
whether the tag must sit inside the interval whose height it supplies.
Figure~\ref{fig:hk-vs-mcshane} shows this tethered-versus-free distinction
directly.
\end{remark*}

\input{tex/figures/hk-vs-mcshane}

\subsection*{Geometric Intuition}

\begin{exposition}
In HK, a tag is a sample point inside the slab. In McShane, a tag is more like
a local address that authorizes nearby slabs. The gauge still says how far the
tag's influence reaches, but the rectangle height may be chosen from a point
near the slab rather than inside it. This makes the integral less forgiving
about sign-changing singular behavior and much closer to Lebesgue's absolute
notion of size.
\end{exposition}

\subsection*{Definition}

\begin{definitionbox}{Definition (McShane-Fine Tagged Partition)}
\begin{definition}[McShane-Fine Tagged Partition]
\label{def:mcshane-fine-tagged-partition}
Let \(\delta:[a,b]\to(0,\infty)\) be a gauge. A finite tagged partition
\(\{([u_i,v_i],\xi_i)\}_{i=1}^n\) is \emph{McShane \(\delta\)-fine} if the
intervals \([u_i,v_i]\) are non-overlapping, cover \([a,b]\), each
\(\xi_i\in[a,b]\), and
\[
  [u_i,v_i]\subset
  \bigl(\xi_i-\delta(\xi_i),\,\xi_i+\delta(\xi_i)\bigr)
  \qquad\text{for every }i.
\]
Unlike an HK tagged partition, the tag \(\xi_i\) is not required to lie in
\([u_i,v_i]\).
\end{definition}
\end{definitionbox}

\begin{remark*}[Standard quantified statement]
\[
\operatorname{IsDeltaFine}((P,\xi),\delta,[a,b])
\Longleftrightarrow
\forall i\;
\bigl(\xi_i\in[a,b]\land [u_i,v_i]\subset
(\xi_i-\delta(\xi_i),\,\xi_i+\delta(\xi_i))\bigr),
\]
with the intervals non-overlapping and covering \([a,b]\).
\end{remark*}

\begin{remark*}[Predicate reading]
\[
\operatorname{IsDeltaFine}((P,\xi),\delta,[a,b])
\Longleftrightarrow
\mathsf{TaggedPartition}((P,\xi),P,[a,b])
\land
\forall i\;
\bigl(\xi_i\in[a,b]\land [u_i,v_i]\subset
(\xi_i-\delta(\xi_i),\,\xi_i+\delta(\xi_i))\bigr).
\]
\end{remark*}

\begin{remark*}[Interpretation]
Figure~\ref{fig:mcshane} isolates the McShane move: a tag may sit outside the
cell whose height it supplies, provided the cell lies inside the tag's gauge
ball. The ruler is still \(\Delta x_i\); the change is entirely in the
admissible tag geometry.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:gauge-on-interval]{Gauge on an Interval}
  \item \hyperref[def:tagged-partition-integration]{Tagged Partition}
\end{itemize}
\end{dependencies}

\input{tex/figures/fig-mcshane}

\begin{definitionbox}{Definition (McShane Integral)}
\begin{definition}[McShane Integral]
\label{def:mcshane-integral}
A function \(f:[a,b]\to\mathbb R\) is \emph{McShane integrable} with value
\(A\) if
\[
  \forall\varepsilon>0\ \exists\delta:[a,b]\to(0,\infty)\ \forall(P,\xi)\,
  \bigl((P,\xi)\text{ is McShane }\delta\text{-fine}
  \Rightarrow |S(f,P,\xi)-A|<\varepsilon\bigr),
\]
where
\[
  S(f,P,\xi)=\sum_i f(\xi_i)(v_i-u_i).
\]
\end{definition}
\end{definitionbox}

\begin{remark*}[Standard quantified statement]
\[
\operatorname{HasDefiniteIntegral}(f,[a,b],\operatorname{McShaneCriterion},A)
\Longleftrightarrow
\forall\varepsilon>0\ \exists\delta:[a,b]\to(0,\infty)\ \forall(P,\xi)\,
\bigl(\operatorname{IsDeltaFine}((P,\xi),\delta,[a,b])
\Rightarrow |S(f,P,\xi)-A|<\varepsilon\bigr).
\]
\end{remark*}

\begin{remark*}[Predicate reading]
\[
  f\colon [a,b]\to\mathbb{R},\\

\operatorname{HasDefiniteIntegral}(f,[a,b],\operatorname{McShaneCriterion},A)
\Longleftrightarrow
\forall\varepsilon>0\ \exists\delta:[a,b]\to(0,\infty)\ \forall(P,\xi)\,
\bigl(\operatorname{IsDeltaFine}((P,\xi),\delta,[a,b])
\Rightarrow |S(f,P,\xi)-A|<\varepsilon\bigr).
\]
\end{remark*}

\begin{remark*}[Interpretation]
Every McShane-fine partition is not necessarily HK-fine, because its tags may
float outside their intervals. But every HK-fine partition is McShane-fine.
Therefore McShane integrability is a stronger demand: the sums must survive
all the usual gauge-fine tests and also the extra free-tag tests.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:mcshane-fine-tagged-partition]{McShane-Fine Tagged Partition}
  \item \hyperref[def:gauge-on-interval]{Gauge on an Interval}
\end{itemize}
\end{dependencies}

\subsection*{Existence and Applicability Criterion}

\begin{theorembox}{Theorem (McShane Sits Between Riemann and HK)}
\begin{theorem}[Riemann Integrable Implies McShane Integrable Implies Henstock--Kurzweil Integrable]
\label{thm:riemann-mcshane-hk-inclusions}
On a compact interval,
\[
  \mathcal R[a,b]\subseteq \mathcal M[a,b]\subseteq \mathcal{HK}[a,b],
\]
and the integral values agree whenever a function belongs to the smaller
class.
\hyperref[prf:riemann-mcshane-hk-inclusions]{\textit{Go to proof.}}
\end{theorem}
\end{theorembox}

\begin{remark*}[Standard quantified statement]
\[
\mathcal R[a,b]\subseteq \mathcal M[a,b]\subseteq \mathcal{HK}[a,b],
\]
with agreeing integral values on the smaller integrability space.
\end{remark*}

\begin{remark*}[Interpretation]
McShane integrability is stronger than HK integrability but includes the
Riemann-integrable functions on compact intervals.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:riemann-integral]{Riemann Integral}
  \item \hyperref[def:mcshane-integral]{McShane Integral}
  \item \hyperref[def:henstock-kurzweil-integral]{Henstock--Kurzweil Integral}
\end{itemize}
\end{dependencies}

\begin{theorembox}{Theorem (McShane Equals Lebesgue)}
\begin{theorem}[McShane Integrability Equals Lebesgue Integrability]
\label{thm:mcshane-equals-lebesgue}
For real-valued functions on a compact interval,
\[
  \mathcal{McShane}[a,b]=\mathcal L[a,b],
\]
and the McShane and Lebesgue integral values agree.
\hyperref[prf:mcshane-equals-lebesgue]{\textit{Go to proof.}}
\end{theorem}
\end{theorembox}

\begin{remark*}[Standard quantified statement]
\[
\mathcal{McShane}[a,b]=\mathcal L[a,b],
\]
and the corresponding integral values agree.
\end{remark*}

\begin{remark*}[Interpretation]
For real-valued functions on a compact interval, the McShane integral recovers
the Lebesgue integral. In practical terms,
\[
  \mathcal M[a,b]=\mathcal L[a,b]
\]
with equal values. Thus McShane is not a second route beyond Lebesgue in the
way HK is. It is a gauge-sum presentation of Lebesgue integration.


Combining the Riemann inclusion, the McShane--Lebesgue identification, and the
HK derivative witness gives
\[
  \mathcal R[a,b]\subsetneq \mathcal{McShane}[a,b]
  =\mathcal L[a,b]\subsetneq\mathcal{HK}[a,b].
\]
The first strict inclusion is the old Riemann failure at dense null
discontinuities; the second is the HK recovery of derivatives whose absolute
size is not Lebesgue integrable.


The proof that every Riemann-integrable function is McShane-integrable uses
the earlier measure-zero diagnosis: Riemann integrability means the
discontinuity set is null. The proof ledger records that McShane imports the
Lebesgue criterion even though its definition belongs syntactically with the
gauge integrals.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:mcshane-integral]{McShane Integral}
  \item \hyperref[thm:lebesgue-criterion-riemann-integrability]{Lebesgue Criterion for Riemann Integrability}
\end{itemize}
\end{dependencies}

\subsection*{Worked Failure Mode}

\begin{remark*}[Interpretation]
The HK derivative example
\[
  F'(x)=2x\sin(1/x^2)-\frac{2}{x}\cos(1/x^2)
\]
is conditionally integrable by HK because the tags remain inside the tiny
slabs where the derivative is being locally linearized. McShane's free tags
can sample nearby oscillatory peaks in a way that destroys this conditional
balance. What survives that stronger test is exactly the Lebesgue-integrable,
absolutely controlled part of the gauge world.
\end{remark*}

\begin{remark*}[Interpretation]
McShane gives a tagged-sum construction of the Lebesgue integral without
starting from simple functions or sigma-algebras. Conceptually, that is its
job in this chapter: it shows that adaptive Riemann-style sums can reach the
Lebesgue class, while HK shows that keeping tags inside slabs reaches beyond
Lebesgue to conditionally integrable derivatives.
\end{remark*}

\subsection*{What the Failure Motivates Next}

\begin{remark*}[Interpretation]
McShane is elegant but not the terminal fix for this chapter's story. If one
wants a tagged-sum definition of the Lebesgue integral, it is excellent. If
one wants the perfect one-dimensional Fundamental Theorem of Calculus, HK is
strictly stronger. And if one wants probability, stochastic processes, and
abstract spaces, the next volume still needs measure theory explicitly.
\end{remark*}

\begin{remark*}[Interpretation]
McShane reveals that gauge machinery and Lebesgue size are compatible. The
next volume builds the measure-theoretic machinery that this chapter has only
anticipated through measure-zero diagnostics and gauge-sum comparisons.
\end{remark*}
