% =========================================================
% Chapter: Functions
% Volume III · Analysis
% =========================================================

\section{Functions}

\begin{tcolorbox}[title={Functions}]
\begin{center}
$\text{Real Analysis}
\;\to\;
\text{Sequences}
\;\to\;
\textbf{Functions}
\;\to\;
\text{Continuity}$
\end{center}
\end{tcolorbox}

\begin{remark*}[Structural Roadmap]
This chapter establishes the vocabulary and foundational theorems
for functions of a real variable. The development proceeds in four
stages. First, the topological infrastructure of $\mathbb{R}$ is
built: $\varepsilon$-neighbourhoods, cluster points, adherent points,
closure, closed sets, and compactness (Heine--Borel). Second,
real-valued functions and their pointwise algebraic operations are
defined and their order-theoretic properties catalogued. Third, the
limit of a function at a cluster point is defined in three equivalent
forms ($\varepsilon$-$\delta$, neighbourhood, sequential), and the
algebra of limits is developed by transfer from the sequences
chapter via the Sequential Criterion. Fourth, one-sided limits and
their relationship to two-sided limits are established.

The chapter depends on: convergence of sequences, the algebra of
sequence limits, the Bolzano--Weierstrass theorem, and the
Axiom of Completeness. It feeds into: continuity (which is the
limit condition applied at points in the domain itself),
differentiation, and the metric space chapter.
\end{remark*}

\input{volume-iii/analysis/functions/notes/index}
\LRAProofsInput{volume-iii/analysis/functions/proofs/index}
