\subsection*{Where This Sits}

Darboux exposed the Riemann disease before measure theory names it precisely:
one uniform fineness parameter must serve the whole interval. There are two
ways forward. Lebesgue will change what is measured. The gauge integrals keep
the tagged-sum picture and change exactly one symbol: the constant fineness
\(\delta>0\) becomes a positive function \(\delta(x)\).

\begin{remark*}[Sibling cure]
Henstock--Kurzweil belongs here, before McShane and the final measure-zero
diagnosis, because it is still visibly a Riemann-style tagged-sum integral.
It patches the uniform-mesh defect without abandoning slabs, tags, or sums.
McShane will modify the tag rule one more time, producing a gauge-sum version
of Lebesgue integration.
\end{remark*}

\subsection*{Geometric Intuition}

A gauge is adaptive mesh refinement written as analysis. It is tiny where the
function needs tight local control and generous where the function is calm. A
tagged slab is allowed only if it fits inside the local radius prescribed by
its own tag.

\begin{remark*}[The one-symbol upgrade]
Riemann uses a positive number:
\[
  \exists\delta>0.
\]
Henstock--Kurzweil uses a positive function:
\[
  \exists\delta:[a,b]\to(0,\infty).
\]
The mesh condition \(\|P\|<\delta\) becomes the local condition that each slab
is \(\delta\)-fine at its tag.
\end{remark*}

\begin{definitionbox}{Definition (Gauge)}
\begin{definition}[Gauge on an Interval]
\label{def:gauge-on-interval}
A \emph{gauge} on \([a,b]\) is a function
\[
  \delta:[a,b]\to(0,\infty).
\]
\end{definition}
\end{definitionbox}

\begin{definitionbox}{Definition (Delta-Fine Tagged Partition)}
\begin{definition}[\(\delta\)-Fine Tagged Partition]
\label{def:delta-fine-tagged-partition}
A tagged partition \((P,\xi)\) is \emph{\(\delta\)-fine} if
\[
  [x_{i-1},x_i]\subset
  \bigl(\xi_i-\delta(\xi_i),\,\xi_i+\delta(\xi_i)\bigr)
  \qquad\text{for every }i.
\]
\end{definition}
\end{definitionbox}

\begin{definitionbox}{Definition (Henstock--Kurzweil Integral)}
\begin{definition}[Henstock--Kurzweil Integral]
\label{def:henstock-kurzweil-integral}
A function \(f:[a,b]\to\mathbb R\) is \emph{Henstock--Kurzweil integrable}
with value \(A\) if
\[
  \forall\varepsilon>0\ \exists\delta:[a,b]\to(0,\infty)\ \forall(P,\xi)\,
  \bigl((P,\xi)\text{ is }\delta\text{-fine}
  \Rightarrow |S(f,P,\xi)-A|<\varepsilon\bigr).
\]
The value is denoted \((\mathrm{HK})\int_a^b f\).
\end{definition}
\end{definitionbox}

\begin{lemmabox}{Lemma (Cousin)}
\begin{lemma}[Cousin's Lemma]
\label{lem:cousin}
For every gauge \(\delta\) on \([a,b]\), there exists a \(\delta\)-fine tagged
partition of \([a,b]\).
\end{lemma}
\end{lemmabox}

\begin{remark*}[Non-vacuity]
Cousin's Lemma prevents the definition from being empty. No matter how wildly
the gauge varies, compactness of \([a,b]\) guarantees that at least one tagged
partition respects all the local step-size demands.
\end{remark*}

\begin{theorembox}{Theorem (Riemann Sits Inside Henstock--Kurzweil)}
\begin{theorem}[Riemann Integrable Implies Henstock--Kurzweil Integrable]
\label{thm:riemann-integrable-implies-hk-integrable}
If \(f\) is Riemann-integrable on \([a,b]\), then \(f\) is
Henstock--Kurzweil integrable on \([a,b]\), and the two integrals have the
same value.
\end{theorem}
\end{theorembox}

\begin{remark*}[Constant gauges]
Riemann is the special case where the gauge is constant. If a Riemann proof
hands over one mesh tolerance \(\delta_0\), the gauge proof uses
\(\delta(x)=\delta_0\) for every \(x\).
\end{remark*}

\begin{lemmabox}{Lemma (Straddle)}
\begin{lemma}[Straddle Lemma]
\label{lem:hk-straddle}
If \(F\) is differentiable at \(\xi\) with \(F'(\xi)=f(\xi)\), then for every
\(\varepsilon>0\) there is \(\delta(\xi)>0\) such that whenever
\(u\le \xi\le v\), \(u,v\in(\xi-\delta(\xi),\xi+\delta(\xi))\),
\[
  |F(v)-F(u)-f(\xi)(v-u)|\le \varepsilon(v-u).
\]
\end{lemma}
\end{lemmabox}

\begin{theorembox}{Theorem (FTC for the Gauge Integral)}
\begin{theorem}[Fundamental Theorem for the Henstock--Kurzweil Integral]
\label{thm:hk-fundamental-theorem}
If \(F:[a,b]\to\mathbb R\) is differentiable at every point and \(F'=f\), then
\(f\) is Henstock--Kurzweil integrable and
\[
  (\mathrm{HK})\int_a^b f=F(b)-F(a).
\]
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Continuous Functions Are Henstock--Kurzweil Integrable)}
\begin{theorem}[Continuous Functions Are Henstock--Kurzweil Integrable]
\label{thm:continuous-hk-integrable}
Every continuous function \(f:[a,b]\to\mathbb R\) is Henstock--Kurzweil
integrable.
\end{theorem}
\end{theorembox}

\begin{remark*}[What it buys]
On a compact interval,
\[
  \mathcal R[a,b]\subsetneq \mathcal M[a,b]=\mathcal L[a,b]
  \subsetneq \mathcal{HK}[a,b].
\]
Figure~\ref{fig:integration-lattice} records this inclusion lattice and the
standard witness at each frontier.
The first strict inclusion is witnessed by functions like
\(\mathbf 1_{\mathbb Q}\), which are Lebesgue-integrable but not Riemann
integrable. The second is witnessed by derivatives such as that of
\(F(x)=x^2\sin(1/x^2)\) with \(F(0)=0\): the derivative is HK-integrable by the
gauge FTC even when its absolute value is not Lebesgue-integrable.

This inclusion statement anticipates the next volume's Lebesgue theory. The
present chapter has not built Lebesgue integration yet; it has only isolated
the Riemann-side machinery, the gauge machinery, and the reason a
measure-theoretic successor is needed.
\end{remark*}

\input{tex/figures/integration-lattice}

\begin{remark*}[Killer example]
Let \(F(x)=x^2\sin(1/x^2)\) for \(x\ne0\), and set \(F(0)=0\). Then \(F\) is
differentiable at \(0\), with \(F'(0)=0\), while for \(x\ne0\),
\[
  F'(x)=2x\sin(1/x^2)-\frac{2}{x}\cos(1/x^2).
\]
The oscillatory term has nonintegrable absolute size near \(0\), so this
derivative is the standard witness that HK reaches beyond Lebesgue while the
FTC remains exact.
\end{remark*}

\begin{remark*}[HK's own bug report]
Henstock--Kurzweil is not simply ``the best integral.'' Lebesgue has stronger
limit theorems, a complete \(L^1\) normed-space home, and a clean abstract
measure-space setting. HK is the jewel for the one-dimensional FTC and
conditional accumulation; Lebesgue and Ito remain the engines for probability
and stochastic integration.
\end{remark*}

\begin{remark*}[Computational bridge]
A gauge \(\delta(x)\) is a spatially varying step-size field. Lipschitz
control is the case where a constant gauge is enough; singular or non-Lipschitz
regions demand a genuinely varying gauge. Cousin's Lemma is the compactness
guarantee that a valid adaptive partition exists.
\end{remark*}

\begin{remark*}[One-page summary]
\[
\begin{array}{c|c|c}
\text{Integral} & \text{Patch} & \text{Remaining defect}\\
\hline
\text{Cauchy} & \text{left rectangles settle for continuous } f &
\text{privileged tag}\\
\text{Riemann} & \text{all tags must agree} &
\text{hard to verify}\\
\text{Darboux} & \text{sup/inf squeeze} &
\text{same class as Riemann}\\
\text{Stieltjes} & \text{change the ruler} &
\text{needs BV; shared jumps}\\
\text{Henstock--Kurzweil} & \text{local gauge fineness} &
\text{weaker limit machinery}\\
\text{McShane} & \text{free gauge tags} &
\text{same class as Lebesgue}\\
\text{Lebesgue} & \text{measure level sets} &
\text{abstract machinery required}
\end{array}
\]
The thread is the right-hand column: every integral is a direct response to a
specific defect.
\end{remark*}
