\newpage
\phantomsection
\label{prf:smoothness-tower}
\LRAProofFor{thm:smoothness-tower}

\begin{remark*}[Return]
\hyperref[thm:smoothness-tower]{Return to Theorem}
\end{remark*}

\begin{theorem*}[The Smoothness Tower]
For every nondegenerate interval \(I\), the inclusions
\[
  C^0(I)\supseteq C^1(I)\supseteq C^2(I)\supseteq \cdots
  \supseteq C^\infty(I)\supseteq C^\omega(I)
\]
hold, and each displayed inclusion is strict.
\end{theorem*}

\begin{proof}[Professional Standard Proof]
\LRAProofBodyStart
If \(f\in C^{k+1}(I)\), then \(f^{(k)}\) is differentiable on \(I\), hence continuous on \(I\). Therefore \(f\in C^k(I)\), so \(C^{k+1}(I)\subseteq C^k(I)\). The inclusion \(C^\infty(I)\subseteq C^k(I)\) is immediate from the definition of \(C^\infty\), and a locally convergent power series is differentiable term by term on a smaller neighbourhood, so \(C^\omega(I)\subseteq C^\infty(I)\).

Strictness is supplied by standard witnesses. Choose an interior point \(a\in I\). For \(k\geq 0\), the function \(\varphi_k(x)=(x-a)^k|x-a|\) is \(C^k\) but not \(C^{k+1}\) at \(a\). For the final inclusion, the translated flat function
\[
  f(x)=
  \begin{cases}
    e^{-1/(x-a)^2}, & x\neq a,\\
    0, & x=a,
  \end{cases}
\]
is \(C^\infty\) and satisfies \(f^{(n)}(a)=0\) for every \(n\). Its Taylor series at \(a\) is therefore the zero series, but \(f(x)>0\) for \(x\neq a\), so \(f\) is not analytic at \(a\).
\end{proof}

\begin{proof}[Detailed Learning Proof]
\LRAProofBodyStart
The inclusions express the meaning of the symbols. Having \(k+1\) continuous derivatives gives \(k\) continuous derivatives by forgetting the last derivative. Having derivatives of every order gives \(k\) derivatives for each fixed \(k\). Being analytic gives a local power-series representation, and power series may be differentiated term by term inside their interval of convergence, so analytic functions are smooth.

The witnesses show that these containments do not collapse into equalities. After translating to an interior point of \(I\), the functions \(x^k|x|\) have exactly the first \(k\) derivatives continuous at the corner, while the next derivative encounters the corner inherited from \(|x|\). The flat function separates smooth from analytic: all derivative data at the flat point vanish, but the function is positive away from that point, so the Taylor series cannot recover the function near it.
\end{proof}

\begin{remark*}[Proof structure]
Prove inclusions directly from definitions, then separate adjacent classes with explicit examples.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:class-ck]{Definition: Class \(C^k\)}
  \item \hyperref[def:class-cinfty]{Definition: Smooth Function; Class \(C^\infty\)}
  \item \hyperref[def:class-comega]{Definition: Real-Analytic Function; Class \(C^\omega\)}
\end{itemize}
\end{dependencies}

\clearpage
