\begin{corollary}[Rational and Irrational Points in Every Open Interval]
\label{cor:every-open-interval-contains-rational-and-irrational}
For every $a,b\in\mathbb{R}$ with $a<b$, there exist
$q\in\mathbb{Q}$ and $s\in\mathbb{R}\setminus\mathbb{Q}$ such that
\[
  a<q<b
  \qquad\text{and}\qquad
  a<s<b.
\]
\hyperref[prf:every-open-interval-contains-rational-and-irrational]{Go to proof.}
\end{corollary}
\end{corollarybox}

\begin{remark*}[Standard quantified statement]
\[
\forall a,b\in\mathbb{R}\;
\Bigl[
a<b\Longrightarrow
\bigl(\exists q\in\mathbb{Q}\;(a<q<b)\land \exists s\in\mathbb{R}\setminus\mathbb{Q}\;(a<s<b)\bigr)
\Bigr].
\]
\end{remark*}

\begin{remark*}[Predicate reading]
\[
P_{\mathbb{R}}=\mathsf{OrderedSet}(\mathbb{R},\leq),\qquad I=\mathbb{R}\setminus\mathbb{Q},\qquad
D_{\mathbb{Q}}=\mathsf{OrderDenseSet}(\mathbb{Q},P_{\mathbb{R}}),\qquad
D_I=\mathsf{OrderDenseSet}(I,P_{\mathbb{R}}),\qquad
\operatorname{IsOrderDenseSubset}(\mathbb{Q},P_{\mathbb{R}})
\land
\operatorname{IsOrderDenseSubset}(I,P_{\mathbb{R}}).
\]
\end{remark*}

\begin{remark*}[Negated quantified statement]
\[
\exists a,b\in\mathbb{R}\;
\Bigl[
a<b\land
\bigl(
\forall q\in\mathbb{Q}\;(q\le a\lor b\le q)
\lor
\forall s\in\mathbb{R}\setminus\mathbb{Q}\;(s\le a\lor b\le s)
\bigr)
\Bigr].
\]
\end{remark*}

\begin{remark*}[Negation predicate reading]
\[
P_{\mathbb{R}}=\mathsf{OrderedSet}(\mathbb{R},\leq),\qquad I=\mathbb{R}\setminus\mathbb{Q},\qquad
D_{\mathbb{Q}}=\mathsf{OrderDenseSet}(\mathbb{Q},P_{\mathbb{R}}),\qquad
D_I=\mathsf{OrderDenseSet}(I,P_{\mathbb{R}}),\qquad
\neg\Bigl[
\operatorname{IsOrderDenseSubset}(\mathbb{Q},P_{\mathbb{R}})
\land
\operatorname{IsOrderDenseSubset}(I,P_{\mathbb{R}})
\Bigr].
\]
\end{remark*}

\begin{remark*}[Failure modes]
\begin{description}
\item[Exposition.]
The corollary fails if a nonempty real interval misses all rational points or misses all irrational points.


  \item[\operatorname{IsOrderDenseSubset}.]
  \[
\exists a,b\in\mathbb{R}\;
\Bigl[
a<b\land
\bigl(
\forall q\in\mathbb{Q}\;(q\le a\lor b\le q)
\lor
\forall s\in\mathbb{R}\setminus\mathbb{Q}\;(s\le a\lor b\le s)
\bigr)
\Bigr].
\]
\[
P_{\mathbb{R}}=\mathsf{OrderedSet}(\mathbb{R},\leq),\qquad I=\mathbb{R}\setminus\mathbb{Q},\qquad
D_{\mathbb{Q}}=\mathsf{OrderDenseSet}(\mathbb{Q},P_{\mathbb{R}}),\qquad
D_I=\mathsf{OrderDenseSet}(I,P_{\mathbb{R}}),\qquad
\neg\Bigl[
\operatorname{IsOrderDenseSubset}(\mathbb{Q},P_{\mathbb{R}})
\land
\operatorname{IsOrderDenseSubset}(I,P_{\mathbb{R}})
\Bigr].
\]
\end{description}
\end{remark*}

\begin{remark*}[Failure modes]
\begin{description}
\item[Exposition.]
\[
\exists a,b\in\mathbb{R}\;(a<b)
\;\land\;
\Bigl[
\underbrace{\forall q\in\mathbb{Q}\;(q\le a\lor b\le q)}_{\text{no rational point}}
\;\lor\;
\underbrace{\forall s\in\mathbb{R}\setminus\mathbb{Q}\;(s\le a\lor b\le s)}_{\text{no irrational point}}
\Bigr].
\]


  \item[\operatorname{IsOrderDenseSubset}.]
  \[
\exists a,b\in\mathbb{R}\;
\Bigl[
a<b\land
\bigl(
\forall q\in\mathbb{Q}\;(q\le a\lor b\le q)
\lor
\forall s\in\mathbb{R}\setminus\mathbb{Q}\;(s\le a\lor b\le s)
\bigr)
\Bigr].
\]
\[
P_{\mathbb{R}}=\mathsf{OrderedSet}(\mathbb{R},\leq),\qquad I=\mathbb{R}\setminus\mathbb{Q},\qquad
D_{\mathbb{Q}}=\mathsf{OrderDenseSet}(\mathbb{Q},P_{\mathbb{R}}),\qquad
D_I=\mathsf{OrderDenseSet}(I,P_{\mathbb{R}}),\qquad
\neg\Bigl[
\operatorname{IsOrderDenseSubset}(\mathbb{Q},P_{\mathbb{R}})
\land
\operatorname{IsOrderDenseSubset}(I,P_{\mathbb{R}})
\Bigr].
\]
\end{description}
\end{remark*}

\begin{remark*}[Interpretation]
The corollary combines the two density theorems. Every real interval, no matter how small, contains representatives of both arithmetic types. Thus neither the rational numbers nor the irrational numbers occupy isolated regions of the real line.
\end{remark*}

\begin{dependencies}
\begin{itemize}
\item \hyperref[def:reals]{Real Numbers}.
\item \hyperref[def:rationals]{Rational Numbers}.
\item \hyperref[def:ordered-set]{Ordered Set}.
\item \hyperref[def:set-difference]{Set Difference}.
\item \hyperref[def:open-interval]{Open Interval}.
\item \hyperref[thm:density-of-rationals-in-reals]{Density of the Rationals}.
\item \hyperref[thm:density-of-irrationals-in-reals]{Density of the Irrationals}.
\end{itemize}
\end{dependencies}





\input{volume-iii/book-analysis-i/bounding/notes/completeness/figure-zoom-invariance}


\begin{exposition}
Density in $\mathbb{R}$ has a scale-invariant consequence: no matter how small a nonempty
open interval becomes, it still contains both rational and irrational points. The interleaving
of $\mathbb{Q}$ and $\mathbb{R}\setminus\mathbb{Q}$ is therefore not a large-scale phenomenon.
It persists at every interval scale.

This has three important consequences. First, the continuum does not become locally discrete
under magnification. For every nonempty open interval $(a,b)$, both
\[
\mathbb{Q}\cap(a,b)
\qquad\text{and}\qquad
(\mathbb{R}\setminus\mathbb{Q})\cap(a,b)
\]
remain nonempty, and in fact infinite. Density is therefore stable under repeated restriction
to smaller intervals.

Second, this behavior sharply distinguishes the real line from discrete numerical models.
Floating-point systems form a discrete set of representable values, so repeated magnification
eventually reaches a scale at which adjacent representable numbers leave no further point
strictly between them. At that stage, interval penetration fails in the discrete model even
though it continues to hold in $\mathbb{R}$.

Third, the Archimedean Property supplies the scale mechanism behind this behavior. Given any
positive scale $\varepsilon$, there exists $n\in\mathbb{N}$ with
\[
\frac{1}{n}<\varepsilon.
\]
This makes it possible to construct rational approximations at arbitrarily small interval
scales, which is one of the basic engines behind density arguments.

The resulting contrast is structural. Smooth mathematical models are built in a setting where
interval penetration persists at every scale, whereas finite computational models eventually
encounter a smallest representable separation. The transition from continuum behavior to
discrete behavior occurs exactly where nonempty intervals in the numerical model cease to
contain further \\representable points.
\end{exposition}

\input{volume-iii/book-analysis-i/bounding/notes/completeness/figure-density-chain}
