\subsection*{Geometric Intuition}

Cauchy makes the simplest possible height choice: always sample the left edge
of each slab. The result is a staircase of left-anchored rectangles. As the
slabs thin out, the question is whether those staircase areas settle.

\begin{remark*}[Engineering reading]
Cauchy's construction is the seed. It answers the geometric problem for the
case where the curve is tame enough that left-edge staircases forget their
initial sampling bias as the mesh shrinks. The construction is deliberately
primitive: it fixes a height rule first and asks for convergence second.
\end{remark*}

\subsection*{Definition}

\begin{definitionbox}{Definition (Cauchy Sum)}
\begin{definition}[Left-Endpoint Cauchy Sum]
\label{def:cauchy-sum}
For \(f:[a,b]\to\mathbb R\) and \(P=\{a=x_0<\cdots<x_n=b\}\), define
\[
  C(f,P)=\sum_{i=1}^{n} f(x_{i-1})\,\Delta x_i.
\]
\end{definition}
\end{definitionbox}

\begin{definitionbox}{Definition (Cauchy Integral)}
\begin{definition}[Cauchy Integral]
\label{def:cauchy-integral}
The function \(f\) is \emph{Cauchy-integrable} with value \(L\) if
\[
  \forall\varepsilon>0\ \exists\delta>0\ \forall P\,
  \bigl(\|P\|<\delta\Rightarrow |C(f,P)-L|<\varepsilon\bigr).
\]
The value \(L\) is denoted \(\int_a^b f(x)\,dx\).
\end{definition}
\end{definitionbox}

\subsection*{Worked Positive Example}

\begin{propositionbox}{Proposition (Integral of a Constant)}
\begin{proposition}[Cauchy Integral of a Constant]
\label{prop:cauchy-integral-constant}
If \(f(x)=c\) on \([a,b]\), then \(\int_a^b c\,dx=c(b-a)\).
\end{proposition}
\end{propositionbox}

\subsection*{Algebraic and Order Properties}

\begin{theorembox}{Theorem (Linearity)}
\begin{theorem}[Linearity of the Cauchy Integral]
\label{thm:cauchy-integral-linearity}
If \(f\) and \(g\) are Cauchy-integrable on \([a,b]\), then
\[
  \int_a^b(\alpha f+\beta g)\,dx
  =
  \alpha\int_a^b f\,dx+\beta\int_a^b g\,dx.
\]
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Monotonicity)}
\begin{theorem}[Monotonicity of the Cauchy Integral]
\label{thm:cauchy-integral-monotonicity}
If \(f\) and \(g\) are Cauchy-integrable on \([a,b]\) and \(f(x)\le g(x)\)
for every \(x\in[a,b]\), then
\[
  \int_a^b f\,dx\le \int_a^b g\,dx .
\]
\end{theorem}
\end{theorembox}

\begin{corollarybox}{Corollary (Bounds)}
\begin{corollary}[Bounds for the Cauchy Integral]
\label{cor:cauchy-integral-bounds}
If \(f\) is continuous on \([a,b]\), \(m=\min_{[a,b]}f\), and
\(M=\max_{[a,b]}f\), then
\[
  m(b-a)\le \int_a^b f\,dx\le M(b-a).
\]
\end{corollary}
\end{corollarybox}

\begin{theorembox}{Theorem (Triangle Inequality)}
\begin{theorem}[Triangle Inequality for the Cauchy Integral]
\label{thm:cauchy-integral-triangle-inequality}
If \(f\) and \(|f|\) are Cauchy-integrable on \([a,b]\), then
\[
  \left|\int_a^b f\,dx\right|\le \int_a^b |f|\,dx .
\]
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Interval Additivity)}
\begin{theorem}[Interval Additivity for the Cauchy Integral]
\label{thm:cauchy-integral-interval-additivity}
If \(c\in[a,b]\) and \(f\) is Cauchy-integrable on the relevant intervals,
then
\[
  \int_a^b f\,dx=\int_a^c f\,dx+\int_c^b f\,dx .
\]
\end{theorem}
\end{theorembox}

\begin{definitionbox}{Definition (Oscillation on an Interval)}
\begin{definition}[Oscillation on an Interval]
\label{def:interval-oscillation-integration}
For bounded \(f\) on an interval \(I\), define
\[
  \omega_f(I)=\sup_I f-\inf_I f.
\]
Oscillation is the error controller: if \(\omega_f(I)\) is small, every sample
height on \(I\) is close to every other sample height.
\end{definition}
\end{definitionbox}

\subsection*{Existence and Applicability Criterion}

\begin{theorembox}{Theorem (Continuous Implies Cauchy-Integrable)}
\begin{theorem}[Continuous Functions Are Cauchy-Integrable]
\label{thm:continuous-cauchy-integrable}
Every continuous function \(f:[a,b]\to\mathbb R\) is Cauchy-integrable.
\end{theorem}
\end{theorembox}

\begin{remark*}[Proof skeleton]
Continuity on the compact interval gives uniform continuity. Hence short slabs
have small oscillation. Given two fine partitions, pass to their common
refinement and compare sums slab by slab; each re-sampling error is bounded by
\(\omega_f(I)\) times the slab width. The sums form a Cauchy net, and
completeness of \(\mathbb R\) supplies the limit.
\end{remark*}

\begin{remark*}[What continuity buys]
Uniform continuity is the load-bearing ingredient. It converts pointwise
control into one global scale: if the slabs are all shorter than that scale,
then every slab has small oscillation. Without this global scale, Cauchy's
left-endpoint definition has no mechanism for proving that unrelated
partitions settle to the same number.
\end{remark*}

\subsection*{Worked Failure Mode}

\begin{remark*}[A first discontinuous edge case]
A single jump should still have an area. If
\[
  f(x)=
  \begin{cases}
    0,&x<c,\\
    1,&x\ge c,
  \end{cases}
\]
on \([a,b]\), the only dangerous slab is the one crossing \(c\). Its total
possible error is bounded by its width, and that width tends to zero as the
mesh tends to zero. This example is not hard; the point is that Cauchy's
definition gives no internal test explaining why it is harmless. The proof
above proves continuity is sufficient, not that controlled discontinuities are
allowed.
\end{remark*}

\subsection*{What the Failure Motivates Next}

\begin{theorembox}{Theorem (Tag Independence)}
\begin{theorem}[Tag Independence for Continuous Functions]
\label{thm:cauchy-tag-independence}
If \(f\) is continuous on \([a,b]\), then every choice of tags gives the same
limit as the left-endpoint sums as \(\|P\|\to 0\).
\end{theorem}
\end{theorembox}

\begin{remark*}[Bug report]
Cauchy has two defects. First, the left endpoint is privileged by convention;
tag independence is a theorem only after continuity has already been assumed.
Second, the existence proof gives no usable criterion for discontinuous
functions. The patch request is to stop privileging the left endpoint and make
tag independence part of the definition.
\end{remark*}

\begin{remark*}[Patch request]
The next definition should not say ``sample on the left.'' It should say:
sample anywhere, even adversarially, and require all fine enough choices to
agree. Riemann is exactly Cauchy's tag-independence theorem promoted into the
definition of integrability.
\end{remark*}
