\newpage
\phantomsection
\label{prf:archimedean-property}
\LRAProofFor{thm:archimedean-property}

\begin{remark*}[Return]
\hyperref[thm:archimedean-property]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Archimedean Property]
For every $x \in \mathbb{R}$, there exists $n \in \mathbb{N}$ such that $n > x$.
\end{theorem*}

\begin{proof}[Professional Standard Proof]
\LRAProofBodyStart
Suppose, toward a contradiction, that the conclusion fails.  Then there is
some $x\in\mathbb{R}$ such that $n\le x$ for every $n\in\mathbb{N}$; that
is, $\mathbb{N}$ is bounded above in $\mathbb{R}$.  By completeness, let
\[
  s=\sup\mathbb{N}.
\]
Since $s-1<s$, the number $s-1$ cannot be an upper bound of $\mathbb{N}$;
otherwise the leastness of $s$ would give $s\le s-1$, impossible.  Hence
there exists $n\in\mathbb{N}$ such that
\[
  n>s-1.
\]
Adding $1$ gives $n+1>s$.  But $n+1\in\mathbb{N}$, and $s$ is an upper bound
of $\mathbb{N}$, so $n+1\le s$.  This contradiction shows that
$\mathbb{N}$ is not bounded above in $\mathbb{R}$.  Therefore for every
$x\in\mathbb{R}$ there exists $n\in\mathbb{N}$ such that $n>x$.
\end{proof}

\begin{proof}[Detailed Learning Proof]
\LRAProofBodyStart
We prove the statement by contradiction.  The theorem says that no real number
can dominate all natural numbers.  Suppose the theorem were false.  Then
there would be some real number $x$ such that
\[
  n\le x
  \qquad\text{for every }n\in\mathbb{N}.
\]
Thus $\mathbb{N}$ would be a nonempty subset of $\mathbb{R}$ that is bounded
above.

By the least upper bound property of $\mathbb{R}$, the set $\mathbb{N}$ would
have a supremum.  Let
\[
  s=\sup\mathbb{N}.
\]
So $s$ is an upper bound for $\mathbb{N}$, and it is the least such upper
bound.

Now consider the smaller number $s-1$.  Because $s-1<s$, it cannot also be an
upper bound of $\mathbb{N}$: if it were, then the leastness of $s$ would force
$s\le s-1$, a contradiction.  Since $s-1$ is not an upper bound, some natural
number lies above it.  Therefore there exists $n\in\mathbb{N}$ such that
\[
  n>s-1.
\]
Adding $1$ to both sides gives
\[
  n+1>s.
\]

But $n+1$ is again a natural number.  Since $s$ is an upper bound of
$\mathbb{N}$, every natural number must be at most $s$, so in particular
\[
  n+1\le s.
\]
This contradicts $n+1>s$.

The contradiction came from assuming that some real number bounds all natural
numbers above.  Hence no such real number exists.  Equivalently, for every
real number $x$, there is a natural number $n$ with $n>x$.
\end{proof}

\begin{remark*}[Proof structure]
Assume $\mathbb{N}$ is bounded above and take its supremum $s$.  Since
$s-1$ is smaller than the least upper bound, it fails to be an upper bound,
so some $n\in\mathbb{N}$ satisfies $n>s-1$.  Then $n+1>s$, contradicting
that $s$ is an upper bound for $\mathbb{N}$.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[ax:completeness-of-reals]{Completeness of the real numbers}.
  \item \hyperref[def:supremum]{Supremum}.
  \item \hyperref[def:upper-bound]{Upper bound}.
\end{itemize}
\end{dependencies}

\clearpage
