% =========================================================
% Completeness and Its Consequences
% =========================================================
\chapter{Bounds}
\section{Completeness of the Real Numbers}



\begin{tcolorbox}[colback=gray!6, colframe=gray!40, arc=2pt,
  left=8pt, right=8pt, top=6pt, bottom=6pt,
  title={\small\textbf{Bounding}},
  fonttitle=\small\bfseries]

\begin{center}
\small
Real Numbers $\;\to\;$ Sequences $\;\to\;$ \textbf{Bounding} $\;\to\;$ Limits of Functions
\end{center}

\medskip
\noindent\textbf{How we got here.}
The chapter depends on the order structure of $\mathbb{R}$, on the language of subsets of
$\mathbb{R}$, and on the distinction between elements of a set and numbers that control the set
from above or below. The earlier development of real-number structure supplies the ambient
ordered field, while the sequence chapter provides the first recurring uses of boundedness as a
hypothesis and as a consequence.

\medskip
\noindent\textbf{What this chapter builds.}
This chapter isolates the language of bounds and extremal control: upper bounds, lower bounds,
bounded above, bounded below, bounded sets, maxima, minima, suprema, and infima. It also
builds the approximation principles attached to least upper bounds and greatest lower bounds,
so that later arguments can move cleanly from order data to existence and convergence
arguments.

\medskip
\noindent\textbf{Where this leads.}
Bounding is the order-theoretic foundation for monotone convergence, extremal arguments,
epsilon-approximation of suprema and infima, and later compactness and continuity results.
It is also the chapter in which the least-upper-bound viewpoint becomes operational rather than
merely axiomatic.

\end{tcolorbox}

\begin{tcolorbox}[colback=gray!6, colframe=gray!40, arc=2pt,
  left=8pt, right=8pt, top=6pt, bottom=6pt,
  title={\small\textbf{Status}},
  fonttitle=\small\bfseries]
\textbf{Planned.} This chapter is currently a structural stub. The chapter scope, section
decomposition, and theorem/dependency order are fixed here before full note expansion.
\end{tcolorbox}

\subsection*{Structural Roadmap}

Each major topic is organised as:
\begin{center}
\textbf{Definitions $\longrightarrow$ Main Theorems $\longrightarrow$ Consequences and Structural Insight}
\end{center}

The global progression is:
\begin{enumerate}
  \item Bounds on subsets of $\mathbb{R}$: upper bounds, lower bounds, bounded above, bounded below, bounded sets.
  \item Extremal elements: maximum and minimum.
  \item Least and greatest extremal bounds: supremum and infimum.
  \item Approximation principles for $\sup A$ and $\inf A$.
  \item Structural consequences: uniqueness, existence under completeness, and preparation for monotone arguments.
\end{enumerate}

\begin{remark}[Primary sources]
This chapter is driven primarily by the order and completeness development in standard real
analysis texts, especially treatments of bounds, supremum, infimum, and the least upper bound
property. The chapter also serves as local infrastructure for later uses in sequences, continuity,
and differentiation.
\end{remark}

\input{volume-iii/analysis/bounding/notes/index}
\input{volume-iii/analysis/bounding/proofs/index}

