
\subsection{Definitions}


\begin{definitionbox}{Definition (Sequence)}
% ---------------------------------------------------------
% Definition: Sequence
% Label: def:sequence
% ---------------------------------------------------------
\begin{definition}[Sequence]
\label{def:sequence}

Let $X$ be a nonempty set. A \textbf{sequence} in $X$ is a function
\[
    x : \mathbb{N} \to X.
\]
The value $x(n)$ is written $x_n$ and called the \textbf{$n$-th term} of the
sequence. The sequence itself is denoted $(x_n)_{n \in \mathbb{N}}$, or
simply $(x_n)$ when the index set is clear.
\end{definition}
\end{definitionbox}

\begin{remark*}[Standard quantified statement]
\[
\forall X \neq \varnothing \;\forall x : \mathbb{N} \to X
\;\bigl(\operatorname{Sequence}(x,X) \Longleftrightarrow x:\mathbb{N}\to X\bigr).
\]
\end{remark*}

\begin{remark*}[Predicate reading]
\[
\operatorname{Sequence}(x_n, X)
\;:=\;
x : \mathbb{N} \to X.
\]
\end{remark*}

\begin{remark*}[Interpretation]
A sequence is not a set of terms but a function: the index carries
independent weight. Two sequences $(x_n)$ and $(y_n)$ in $X$ are equal
precisely when $x_n = y_n$ for every $n \in \mathbb{N}$, so order and
repetition are intrinsic to the object. The notational collapse from
$x(n)$ to $x_n$ is conventional suppression of function-application
syntax; the underlying object remains a function $\mathbb{N} \to X$.
When $X = \mathbb{R}$, the sequence is called a \textbf{real sequence},
which is the default ambient context for this chapter.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:function]{Function}
  \item \hyperref[def:natural-numbers]{Natural Numbers}
\end{itemize}
\end{dependencies}

\begin{definitionbox}{Definition (Real Sequence)}
% ---------------------------------------------------------
% Definition: Real Sequence
% Label: def:real-sequence
% ---------------------------------------------------------
\begin{definition}[Real Sequence]
\label{def:real-sequence}

A \textbf{real sequence} is a sequence whose image is contained in
$\mathbb{R}$. Equivalently, a real sequence is a function
\[
    x : \mathbb{N} \to \mathbb{R}.
\]
\end{definition}
\end{definitionbox}

\begin{remark*}[Standard quantified statement]
\[
\operatorname{RealSequence}(x_n)
\Longleftrightarrow
x:\mathbb{N}\to\mathbb{R}.
\]
\end{remark*}

\begin{remark*}[Predicate reading]
\[
\operatorname{RealSequence}(x_n)
\;:=\;
\operatorname{Sequence}(x_n,\mathbb{R}).
\]
\end{remark*}

\begin{remark*}[Interpretation]
A real sequence is not a new kind of indexing object; it is the
specialization of a sequence to the ambient space $\mathbb{R}$. Thus the
generic function structure is inherited from sequences, while order,
absolute value, and arithmetic enter through the real codomain.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:sequence]{Sequence}
  \item \hyperref[def:reals]{Real Numbers}
\end{itemize}
\end{dependencies}

\begin{example*}[Constant Sequence]
\label{ex:constant-sequence}

Let $c \in \mathbb{R}$. The \textbf{constant sequence} is defined by
\[
    x_n := c \quad \forall n \in \mathbb{N}.
\]
The constant sequence converges to $c$: given any $\varepsilon > 0$,
take $N = 1$, and observe $|x_n - c| = 0 < \varepsilon$ for all $n \ge 1$.
It is the degenerate case of convergence in which the tail is not merely
eventually close to $L$ but identically equal to it from the first term.
\end{example*}

\begin{example*}[The Sequence $(1/n)$]
\label{ex:sequence-reciprocal}

The sequence $(x_n)$ defined by
\[
    x_n := \frac{1}{n} \quad \forall n \in \mathbb{N}
\]
converges to $0$. Given $\varepsilon > 0$, the Archimedean property
supplies $N \in \mathbb{N}$ with $N > 1/\varepsilon$, and then for all
$n \ge N$,
\[
    \left|\frac{1}{n} - 0\right| = \frac{1}{n} \le \frac{1}{N} < \varepsilon.
\]
This is the canonical example of a sequence that approaches its limit
monotonically from above, never reaching it. It also serves as the
standard witness in squeeze arguments and in the proof that
$\inf\{1/n : n \in \mathbb{N}\} = 0$.
\end{example*}

\begin{example*}[The Sequence $(n)$]
\label{ex:sequence-natural}

The sequence $(x_n)$ defined by
\[
    x_n := n \quad \forall n \in \mathbb{N}
\]
is divergent. For any proposed limit $L \in \mathbb{R}$, take
$\varepsilon = 1$; the Archimedean property supplies $n \in \mathbb{N}$
with $n > L + 1$, so $|x_n - L| = |n - L| > 1 = \varepsilon$ for
infinitely many $n$. The sequence is unbounded, and every convergent
sequence is bounded, so divergence also follows from that theorem once
it is established. This is the canonical example of divergence to
$+\infty$: the terms are not oscillating outside a neighborhood of $L$
but growing without bound in a single direction.
\end{example*}



































































