% =========================================================
% Sub-index: limits
% Volume III $\cdot$ Analysis $\cdot$ Functions
% =========================================================

\section{Limits}

\begin{toolkitbox}{Toolkit --- One-Sided Limits}
\begin{itemize}
  \item $\operatorname{RightLimit}(f,c,L)$: approach from $x>c$ only.
    Input condition: $0<x-c<\delta$.
  \item $\operatorname{LeftLimit}(f,c,L)$: approach from $x<c$ only.
    Input condition: $0<c-x<\delta$.
  \item Sequential criteria hold for each direction separately.
  \item $\operatorname{FunctionLimit}(f,c,L)\iff
    \operatorname{RightLimit}(f,c,L)\wedge\operatorname{LeftLimit}(f,c,L)$.
\end{itemize}
\end{toolkitbox}


\begin{toolkitbox}{Toolkit --- Limits of Functions}
\begin{itemize}
  \item $\lim_{x \to c} f(x) = L$ requires $c$ to be a cluster point
    of $\operatorname{dom}(f)$. The value $f(c)$ is irrelevant;
    $f$ need not be defined at $c$.
  \item The input condition is punctured:
    $0<|x-c|<\delta$ means
    $0 < |x-c| < \delta$. This is what separates limits from
    continuity, where $\operatorname{Within}(x,c,\delta)$
    permits $x = c$.
  \item Three equivalent forms: $\varepsilon$-$\delta$, neighbourhood,
    sequential. The Sequential Criterion is the primary working tool.
  \item Bridge principle: algebra of sequence limits transfers
    automatically via the Sequential Criterion.
  \item A finite limit implies $\exists\delta>0\;\exists M>0\;\forall x\in A\;(0<|x-c|<\delta\Rightarrow |f(x)|\leq M)$.
  \item Limits are local: behavior far from $c$ is irrelevant.
\end{itemize}
\end{toolkitbox}


\begin{toolkitbox}{Toolkit --- Algebra of Limits}
\begin{itemize}
  \item All five rules follow from the Sequential Criterion plus
    algebra of sequence limits. No new $\varepsilon$-$\delta$ work.
  \item Bridge: $(x_n)\subseteq A\setminus\{c\}$, $x_n\to c$
    $\Rightarrow$ $f(x_n)\to L$, $g(x_n)\to M$
    $\Rightarrow$ apply sequence algebra
    $\Rightarrow$ lift back by Sequential Criterion.
  \item Quotient: $M\neq 0$ forces $\operatorname{BoundedAwayFromZeroNear}(g,c)$,
    making $f/g$ well-defined on a punctured neighbourhood.
\end{itemize}
\end{toolkitbox}


\input{volume-iii/analysis/functions/notes/limits/notes-limits}
\input{volume-iii/analysis/functions/notes/limits/notes-algebra-of-limits}
\input{volume-iii/analysis/functions/notes/limits/notes-one-sided-limits}
