% =========================================================
% Sub-index: point-continuity
% Volume III - Analysis - Continuity
% =========================================================

\section{Point Continuity}

\begin{toolkitbox}{Toolkit --- Oscillation}
\begin{itemize}
  \item $\operatorname{OscillationOn}(f,E,\omega)$:
    $\omega(f;E)=\sup_{x_1,x_2\in E}|f(x_1)-f(x_2)|=\operatorname{diam}(f(E))$.
  \item $\operatorname{OscillationAt}(f,x_0,\omega)$:
    $\omega(f;x_0)=\lim_{\delta\to 0^+}\omega(f;U_\delta(x_0)\cap E)$.
    The limit exists because the function $\delta\mapsto\omega(f;U_\delta(x_0)\cap E)$
    is nonincreasing.
  \item $\operatorname{ContinuousAt}(f,x_0)\iff\omega(f;x_0)=0$.
  \item Discontinuity set: $D(f)=\{x:\omega(f;x)>0\}=
    \bigcup_{n=1}^\infty\{x:\omega(f;x)\geq 1/n\}$.
  \item Each threshold set is closed; $D(f)$ is $F_\sigma$.
\end{itemize}
\end{toolkitbox}


\begin{toolkitbox}{Toolkit --- Discontinuity}
\begin{itemize}
  \item $\operatorname{DiscontinuousAt}(f,a)$ is the negation of $\operatorname{ContinuousAt}(f,a)$.
  \item Quantifier reversal governs failure of continuity.
  \item Three equivalent formulations: $\varepsilon$-$\delta$, sequential, neighbourhood.
  \item Taxonomy: removable, jump, essential.
\end{itemize}
\end{toolkitbox}


\begin{toolkitbox}{Toolkit --- Continuity}
\begin{itemize}
  \item Three equivalent forms: $\varepsilon$-$\delta$, neighbourhood,
    sequential. The $\varepsilon$-$\delta$ form is unpunctured
    ($x=c$ allowed), unlike function limits.
  \item $\delta$ may depend on both $\varepsilon$ and $c$.
    If $\delta$ depends only on $\varepsilon$, the condition is
    uniform continuity.
  \item Isolated points are automatically continuous.
  \item Algebra: sums, differences, products, scalar multiples,
    and quotients (denominator nonzero) of continuous functions
    are continuous.
  \item Composition preserves continuity.
\end{itemize}
\end{toolkitbox}


\input{volume-iii/book-analysis-ii/continuity/notes/point-continuity/notes-continuity}
\input{volume-iii/book-analysis-ii/continuity/notes/point-continuity/notes-discontinuity}
\input{volume-iii/book-analysis-ii/continuity/notes/point-continuity/notes-oscillation}
