% =========================================================
% Notes Index --- Continuity Chapter
% Volume III - Analysis
% =========================================================

% ---------------------------------------------------------
% Breadcrumb
% ---------------------------------------------------------
\section{Continuity}
\begin{tcolorbox}[title={Continuity}]
\begin{center}
$\text{Bounding}
\;\to\;
\textbf{Continuity}
\;\to\;
\text{Differentiation}$
\end{center}
\end{tcolorbox}

\vspace{1em}

% ---------------------------------------------------------
% Structural Roadmap
% ---------------------------------------------------------

\begin{remark*}[Structural Roadmap]
This chapter formalizes the notion of a function that respects
neighborhood structure. The $\varepsilon$-$\delta$ definition,
the three equivalent formulations, and the algebra of continuous
functions are established first. The local theory --- boundedness,
sign stability, composition --- then leads to the global results:
the Extreme Value Theorem, the Intermediate Value Theorem, and
the Preservation of Intervals. Uniform continuity is developed
as the global upgrade of pointwise continuity, with Heine--Cantor
as the principal theorem. The Lipschitz and bi-Lipschitz hierarchies
provide quantitative refinements. Monotone functions and their
discontinuity structure, oscillation theory, and the gauge method
complete the chapter. The approximation section culminates in the
Weierstrass and Bernstein theorems.

The chapter depends on: convergence of sequences (Chapter:
sequences), the algebra of limits of functions (Chapter:
functions), and the completeness of $\mathbb{R}$ via the
Bolzano--Weierstrass theorem (Chapter: real-analysis).
It feeds into: differentiation (which requires continuity as a
precondition), Riemann integration (which uses uniform continuity
and the approximation theorems), and metric space topology.
\end{remark*}

\vspace{1em}

% ---------------------------------------------------------
% Section inputs --- dependency order
% ---------------------------------------------------------

\input{volume-iii/analysis/continuity/notes/point-continuity/index}
\input{volume-iii/analysis/continuity/notes/global-theorems/index}
\input{volume-iii/analysis/continuity/notes/uniform-continuity/index}
\input{volume-iii/analysis/continuity/notes/monotone-functions/index}
\input{volume-iii/analysis/continuity/notes/limits-at-infinity/index}
\input{volume-iii/analysis/continuity/notes/approximation/index}
\input{volume-iii/analysis/continuity/notes/gauge/index}
