\subsection*{Geometric Intuition}

Darboux integrability fails where upper and lower staircases refuse to meet.
That refusal is local oscillation. Thus the exact Riemann question becomes:
how large is the set where \(f\) is discontinuous?

\begin{remark*}[Engineering reading]
This final section is not another integral. It is the diagnostic scan of the
entire Riemann--Darboux family, placed immediately after Darboux so the exact
obstruction is named before the chapter turns to weighted and gauge variants.
Once Darboux has made the gap visible, the remaining question is
whether the bad part of the domain is small enough to cover by slabs of
negligible total length.
\end{remark*}

\subsection*{Definition}

\begin{definitionbox}{Definition (Measure Zero)}
\begin{definition}[Measure Zero]
\label{def:measure-zero}
A set \(E\subseteq\mathbb R\) has \emph{measure zero} if for every
\(\varepsilon>0\) there are open intervals \(I_k\) such that
\[
  E\subseteq\bigcup_{k=1}^{\infty}I_k,
  \qquad
  \sum_{k=1}^{\infty}|I_k|<\varepsilon.
\]
\end{definition}
\end{definitionbox}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:open-set]{Open Set}
\end{itemize}
\end{dependencies}

\begin{definitionbox}{Definition (Point Oscillation)}
\begin{definition}[Point Oscillation]
\label{def:point-oscillation-integration}
For bounded \(f\) on \([a,b]\), define
\[
  \omega_f(x)=
  \inf_{\delta>0}
  \omega_f\bigl((x-\delta,x+\delta)\cap[a,b]\bigr).
\]
Then \(f\) is continuous at \(x\) exactly when \(\omega_f(x)=0\).
\end{definition}
\end{definitionbox}

\begin{remark*}[Oscillation levels]
The sets
\[
  D_\eta=\{x:\omega_f(x)\ge \eta\}
\]
separate the bad set by severity. The full discontinuity set is
\[
  D=\bigcup_{k=1}^{\infty}D_{1/k}.
\]
The proof of the criterion works by showing that positive-size high
oscillation forces a permanent Darboux gap, while null high-oscillation sets
can be covered by intervals of tiny total length.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:function-bounded]{Bounded Function}
  \item \hyperref[def:interval-oscillation-integration]{Interval Oscillation}
  \item \hyperref[def:oscillation-at-a-point]{Oscillation at a Point}
\end{itemize}
\end{dependencies}

\subsection*{Existence and Applicability Criterion}

\begin{theorembox}{Theorem (Lebesgue Criterion)}
\begin{theorem}[Lebesgue Criterion for Riemann Integrability]
\label{thm:lebesgue-criterion-riemann-integrability}
A bounded function \(f:[a,b]\to\mathbb R\) is Riemann-integrable if and only
if its discontinuity set
\[
  D=\{x\in[a,b]:\omega_f(x)>0\}
\]
has measure zero.
\hyperref[prf:lebesgue-criterion-riemann-integrability]{\textit{Go to proof.}}
\end{theorem}
\end{theorembox}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:function-bounded]{Bounded Function}
  \item \hyperref[def:riemann-integral]{Riemann Integral}
  \item \hyperref[def:measure-zero]{Measure Zero}
  \item \hyperref[def:point-oscillation-integration]{Point Oscillation}
\end{itemize}
\end{dependencies}

\subsection*{Worked Failure Mode and Handoff}

\begin{remark*}[Terminal diagnosis]
Riemann integration works precisely when the set of bad points is invisible to
length. The Dirichlet function \(\mathbf 1_{\mathbb Q}\) is discontinuous
everywhere, so \(D=[0,1]\), not a null set. The Lebesgue patch is to stop
partitioning the domain into slabs and instead measure the sets where the
function takes given ranges of values. Henstock--Kurzweil keeps tagged sums,
but replaces uniform fineness by local fineness; McShane shows that a slightly
stricter gauge rule recovers the Lebesgue class itself. The pathology plate
in Figure~\ref{fig:failures-atlas} is the visual companion to this diagnosis.
\end{remark*}

\begin{remark*}[Lebesgue handoff]
The slogan is precise: Riemann partitions the domain, so every slab that meets
a dense bad set still sees the bad behavior. Lebesgue partitions the range:
it groups points by height and measures the set carrying each height. For
\(\mathbf 1_{\mathbb Q}\), the height \(1\) lives on a null set and therefore
contributes nothing.
\end{remark*}

\input{tex/exposition/integration-failures}
\input{tex/exposition/gauge-integrals}
