\begin{theorem}[Standard Completeness Equivalences]
\label{thm:standard-completeness-equivalences}
Let $F$ be an Archimedean linearly ordered field.  The following statements are
equivalent:
\begin{enumerate}[label=(\roman*)]
  \item $F$ has the least upper bound property.
  \item $F$ has the greatest lower bound property.
  \item Every increasing sequence in $F$ that is bounded above converges, and
  every decreasing sequence in $F$ that is bounded below converges.
  \item Every nested sequence of nonempty closed bounded intervals in $F$ has
  nonempty intersection.
  \item Every Cauchy sequence in $F$ converges in $F$.
  \item Every bounded sequence in $F$ has a convergent subsequence.
\end{enumerate}

\smallskip
\noindent
\hyperref[prf:standard-completeness-equivalences]{\textit{Go to proof.}}
\end{theorem}
\end{theorembox}

\begin{remark*}[Standard quantified statement]
\[
\text{LUB property}
\Longleftrightarrow
\text{monotone convergence}
\Longleftrightarrow
\text{nested intervals}
\Longleftrightarrow
\text{Bolzano--Weierstrass}
\Longleftrightarrow
\text{Cauchy completeness}.
\]
\end{remark*}

\begin{remark*}[Interpretation]
The first statement is the order version. The second and fifth are sequence
versions. The third is the interval version. The fourth is the compactness
version for bounded sequences.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:real-sequence]{Real Sequence}
  \item \hyperref[def:sequence]{Sequence}
  \item \hyperref[def:subsequence-of-sequence]{Subsequence}
  \item \hyperref[def:convergent-sequence]{Convergent Sequence}
  \item \hyperref[def:closed-interval]{Closed Interval}
  \item \hyperref[def:cauchy-sequence]{Cauchy Sequence}
  \item \hyperref[def:monotone-sequence]{Monotone Sequence}
  \item \hyperref[def:bounded-sequence]{Bounded Sequence}
  \item \hyperref[def:least-upper-bound-property]{Least Upper Bound Property}
  \item \hyperref[thm:monotone-convergence-theorem]{Monotone Convergence Theorem}
  \item \hyperref[thm:nested-interval-theorem]{Nested Interval Theorem}
  \item \hyperref[thm:bolzano-weierstrass-sequences]{Bolzano--Weierstrass Theorem for Sequences}
  \item \hyperref[thm:cauchy-criterion-real-sequences]{Cauchy Criterion for Real Sequences}
\end{itemize}
\end{dependencies}
