% =========================================================
% Section: Carath\'{e}odory Factorization and Chain Rule
% =========================================================
\subsection{Carath\'{e}odory Characterization}

% ---------------------------------------------------------

\begin{remark*}[Interpretation]
Carath\'{e}odory replaces division by factorisation:
\(f(x)-f(c)=(x-c)\varphi(x)\), with \(\varphi\) continuous at \(c\).
Differentiability becomes continuity of the slope factor, and continuity
composes. That is why the chain rule becomes clean rather than a fight with
vanishing denominators.
\end{remark*}

\begin{definitionbox}{Definition (Carath\'{e}odory Factorization)}
\begin{definition}[Carath\'{e}odory Factorization]
\label{def:caratheodory-factorization}
Let $I \subseteq \mathbb{R}$ be an interval, let $f : I \to \mathbb{R}$, and let $c \in I$. We say that $f$ admits a \emph{Carath\'{e}odory factorization} at $c$ if there exists a function $\phi : I \to \mathbb{R}$, continuous at $c$, such that
\[
f(x) = f(c) + (x-c)\,\phi(x) \qquad \text{for all } x \in I.
\]
In this case, $f$ is differentiable at $c$ and $f'(c) = \phi(c)$.
\end{definition}
\end{definitionbox}

\begin{remark*}[Standard quantified statement]
\[
\exists \phi : I \to \mathbb{R}\;
\bigl(\operatorname{IsContinuous}(\phi,c)
\;\land\;
\forall x \in I\;[f(x) = f(c)+(x-c)\phi(x)]\bigr).
\]
\end{remark*}

\begin{remark*}[Predicate reading]
The existence of a Carath\'{e}odory factorization at $c$ is equivalent to $\operatorname{IsDifferentiable}(f,c)$ by the characterization theorem below. The factorizing function is explicit:
\[
\phi(x) =
\begin{cases}
\dfrac{f(x)-f(c)}{x-c} & x \neq c, \\[6pt]
f'(c) & x = c.
\end{cases}
\]
Differentiability of $f$ at $c$ is precisely the statement that this piecewise-defined $\phi$ is continuous at $c$.
\end{remark*}

\begin{remark*}[Interpretation]
The Carath\'{e}odory factorization replaces the difference quotient --- a function with a removable discontinuity at $c$ --- with a function $\phi$ that is genuinely continuous at $c$. The factorization $f(x)-f(c) = (x-c)\phi(x)$ holds everywhere on $I$, including at $x=c$ where both sides equal zero. The derivative is recovered as $\phi(c)$ without ever dividing by zero. This reframing converts analytical limit conditions into topological continuity conditions, which compose and factor more cleanly. It is the preferred tool for proving the product rule, quotient rule, and chain rule, because continuity of a product or composition is easier to establish than the existence of a limit of a quotient.

\medskip
\textbf{Carath\'{e}odory vs.\ Lipschitz.} Both control the increment $f(x)-f(c)$ by the factor $(x-c)$, but differently. The Carath\'{e}odory factorization requires the slope function $\phi(x)$ to extend \emph{continuously} to $c$; it controls the \emph{behaviour} of the slope, not just its size. The Lipschitz condition $|f(x)-f(c)| \leq L|x-c|$ only bounds the size of the increment. Carath\'{e}odory implies Lipschitz: if $\phi$ is continuous at $c$ it is bounded near $c$, so $|f(x)-f(c)| = |\phi(x)||x-c| \leq K|x-c|$ for some $K$ near $c$. The converse fails: $f(x)=|x|$ is Lipschitz on $\mathbb{R}$ with constant $1$ but the slope function takes values $\pm 1$ on either side of $0$ with no continuous extension.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:derivative-at-a-point]{Definition: Derivative at a Point}
  \item \hyperref[def:continuous-at-point]{Definition: Continuous at a Point}
\end{itemize}
\end{dependencies}

% ---------------------------------------------------------

\begin{theorembox}{Theorem}
\begin{theorem}[Carath\'{e}odory Characterization of Differentiability]
\label{thm:caratheodory-characterization-of-differentiability}
Let $I \subseteq \mathbb{R}$ be an interval, let $f : I \to \mathbb{R}$, and let $c \in I$. The following are equivalent:
\begin{enumerate}[label=(\roman*)]
\item $f$ is differentiable at $c$.
\item There exists a function $\phi : I \to \mathbb{R}$, continuous at $c$, such that
\[
f(x) = f(c) + (x-c)\,\phi(x) \qquad \text{for all } x \in I.
\]
\end{enumerate}
In this case, $\phi(c) = f'(c)$.
\hyperref[prf:caratheodory-characterization-of-differentiability]{Go to proof.}
\hyperref[prf:caratheodory-characterization-of-differentiability]{Go to proof.}
\end{theorem}
\end{theorembox}

\begin{remark*}[Standard quantified statement]
\begin{align*}
\operatorname{IsDifferentiable}(f,c)
\;&\iff\;
\exists\phi:I\to\mathbb{R}\;
\bigl(\operatorname{IsContinuous}(\phi,c)\\
&\quad\land\;\forall x \in I\;[f(x)=f(c)+(x-c)\phi(x)]\bigr).
\end{align*}
In this case $\phi(c) = f'(c)$.
\end{remark*}

\begin{remark*}[Interpretation]
This theorem establishes that differentiability and the existence of a Carath\'{e}odory factorization are exactly the same condition. The proof is a two-direction construction: in the forward direction, define $\phi$ as the difference quotient extended by $f'(c)$ at $c$ and verify continuity from the definition of the derivative; in the backward direction, recover the difference quotient from $\phi$ and read off its limit as $\phi(c)$. The theorem's power is that it converts every future differentiability argument into a continuity argument: to show $g \circ f$ is differentiable, find a continuous Carath\'{e}odory function for it; composing the Carath\'{e}odory functions of $f$ and $g$ yields one automatically.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:caratheodory-factorization]{Definition: Carath\'{e}odory Factorization}
  \item \hyperref[def:derivative-at-a-point]{Definition: Derivative at a Point}
  \item \hyperref[def:continuous-at-point]{Definition: Continuous at a Point}
\end{itemize}
\end{dependencies}
