\section*{Appendix: The Gauge Integrals}

\begin{remark*}[Source placement]
This appendix is the converted support note from \texttt{gauge-integrals.tex}.
The standalone preamble, local theorem declarations, and duplicate figure
includes have been removed; the shared figures are the pinned figures already
included in Sections~1.6 and~1.7.
\end{remark*}

\begin{remark*}[The gauge framework]
The gauge integrals replace Riemann's single global mesh tolerance by a local
step-size controller \(\delta:[a,b]\to(0,\infty)\). Henstock--Kurzweil and
McShane then differ by one geometric clause. HK requires the tag to sit inside
the interval it controls. McShane drops that tether and allows the tag to
range over \([a,b]\), provided the interval lies inside the tag's gauge ball.
The contrast is visualized in Figures~\ref{fig:hk-vs-mcshane} and
\ref{fig:mcshane}.
\end{remark*}

\begin{remark*}[Free tags and Lebesgue]
McShane's free tags force absolute, Lebesgue-style behavior. Since a tag can
authorize nearby intervals without lying inside them, the sums can test
whether the mass assigned to height bands is genuinely controlled. On compact
intervals this recovers the Lebesgue integral: \(\mathcal M[a,b]=\mathcal
L[a,b]\), with equal values.
\end{remark*}

\begin{remark*}[Tethered tags and the FTC]
HK keeps the tag tethered to its interval, which preserves local cancellation
for derivatives. That is why the HK integral has the exact one-dimensional
FTC: if \(F\) is differentiable everywhere, then \(F'\) is HK-integrable and
\((\mathrm{HK})\int_a^b F'=F(b)-F(a)\), even when \(F'\) is not Lebesgue
integrable.
\end{remark*}

\begin{remark*}[Lattice]
The resulting compact-interval lattice is
\[
  \mathcal R[a,b]\subsetneq \mathcal L[a,b]=\mathcal M[a,b]
  \subsetneq \mathcal{HK}[a,b],
\]
as recorded in Figure~\ref{fig:integration-lattice}. This appendix is kept
after the main chapter because the book has not yet built the measure theory
needed to prove the McShane--Lebesgue identification.
\end{remark*}
