\section*{Structural Atlas Appendix: Pathologies of the Riemann Integral}

\begin{remark*}[Source placement]
This appendix is the converted support note from
\texttt{integration-failures.tex}. Its standalone theorem machinery and
document preamble have been removed; the material is kept as commentary so it
does not duplicate the formal Lebesgue criterion in
Section~\ref{thm:lebesgue-criterion-riemann-integrability}.
\end{remark*}

\begin{remark*}[The one theorem behind the failures]
The Riemann failures in Figure~\ref{fig:failures-atlas} are not a bag of
examples. They are tests against the two hypotheses in the Lebesgue criterion:
boundedness, and a discontinuity set of measure zero. Dirichlet fails because
its discontinuity set is all of \([0,1]\). Unbounded examples fail before the
criterion even begins. Pointwise limits expose a different weakness: the
Riemann class is not stable under the limit operations that Lebesgue
integration was built to support.
\end{remark*}

\begin{remark*}[Thomae as the diagnostic example]
Thomae's function is the useful warning. Its discontinuities are dense, but
they are countable and therefore null. Darboux can isolate the finitely many
large spikes above any fixed threshold inside intervals of tiny total length;
outside those intervals, the upper sums are uniformly small. Thus density of
the bad set is not the obstruction. Size is.
\end{remark*}

\begin{remark*}[Through-line]
The atlas failure note should be read as the bridge from Darboux to Measure
Zero: \(U(f,P)-L(f,P)\) is local oscillation times length, so the only bad
oscillation that matters is bad oscillation carried by a set of positive
length. That observation closes the Riemann family and points directly to
Lebesgue's range-partition construction.
\end{remark*}

