\subsection*{Geometric Intuition}

Riemann and Darboux weigh each slab by ordinary length, \(\Delta x_i\).
Riemann--Stieltjes changes the ruler. A slab is weighed by how much an
integrator \(\alpha\) changes across it:
\[
  \Delta\alpha_i=\alpha(x_i)-\alpha(x_{i-1}).
\]
If \(\alpha(x)=x\), ordinary Riemann integration returns. If \(\alpha\) jumps,
the integral sees a point mass.

\begin{remark*}[Engineering reading]
Stieltjes does not repair the discontinuity-set problem. It answers a
different complaint: ordinary integration has only one ruler. By replacing
\(\Delta x_i\) with \(\Delta\alpha_i\), the integral can count regions with
nonuniform weight and can encode discrete masses as jumps of \(\alpha\).
\end{remark*}

\begin{definitionbox}{Definition (Total Variation)}
\begin{definition}[Total Variation]
\label{def:total-variation}
The total variation of \(\alpha\) on \([a,b]\) is
\[
  V_a^b(\alpha)=\sup_P\sum_i |\alpha(x_i)-\alpha(x_{i-1})|.
\]
\end{definition}
\end{definitionbox}

\begin{definitionbox}{Definition (Bounded Variation)}
\begin{definition}[Bounded Variation]
\label{def:bounded-variation-integration}
The function \(\alpha\) has \emph{bounded variation} on \([a,b]\) if
\[
  V_a^b(\alpha)<\infty.
\]
Geometrically, this says the ruler has finite total up-and-down travel.
\end{definition}
\end{definitionbox}

\begin{propositionbox}{Proposition (Monotone Implies BV)}
\begin{proposition}[Monotone Functions Have Bounded Variation]
\label{prop:monotone-bounded-variation}
If \(\alpha\) is monotone on \([a,b]\), then \(\alpha\) has bounded variation.
\end{proposition}
\end{propositionbox}

\begin{remark*}[Why bounded variation is the honest ruler condition]
If \(\alpha\) is increasing, the increments telescope:
\[
  \sum_i\bigl(\alpha(x_i)-\alpha(x_{i-1})\bigr)=\alpha(b)-\alpha(a).
\]
Bounded variation is the signed analogue of that finite ruler budget. It is
what prevents the weighted sums from accumulating uncontrolled oscillatory
ruler error.
\end{remark*}

\begin{definitionbox}{Definition (Riemann--Stieltjes Integral)}
\begin{definition}[Riemann--Stieltjes Integral]
\label{def:riemann-stieltjes-integral}
The Riemann--Stieltjes sum is
\[
  \sum_i f(\xi_i)\bigl(\alpha(x_i)-\alpha(x_{i-1})\bigr).
\]
When these sums have a tag-independent limit as \(\|P\|\to0\), the limit is
denoted \(\int_a^b f\,d\alpha\).
\end{definition}
\end{definitionbox}

\begin{theorembox}{Theorem (Continuous Integrand, BV Integrator)}
\begin{theorem}[Continuous Integrand and BV Integrator]
\label{thm:rs-continuous-bv-existence}
If \(f\) is continuous on \([a,b]\) and \(\alpha\) has bounded variation, then
\(\int_a^b f\,d\alpha\) exists.
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Bilinearity)}
\begin{theorem}[Bilinearity of the Riemann--Stieltjes Integral]
\label{thm:rs-bilinearity}
Whenever the displayed integrals exist,
\[
  \int_a^b (\lambda f+\mu g)\,d\alpha
  =
  \lambda\int_a^b f\,d\alpha+\mu\int_a^b g\,d\alpha
\]
and
\[
  \int_a^b f\,d(\lambda\alpha+\mu\beta)
  =
  \lambda\int_a^b f\,d\alpha+\mu\int_a^b f\,d\beta .
\]
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Interval Additivity)}
\begin{theorem}[Interval Additivity for the Riemann--Stieltjes Integral]
\label{thm:rs-interval-additivity}
If \(c\in[a,b]\) and the relevant Riemann--Stieltjes integrals exist, then
\[
  \int_a^b f\,d\alpha
  =
  \int_a^c f\,d\alpha+\int_c^b f\,d\alpha .
\]
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Integration by Parts)}
\begin{theorem}[Riemann--Stieltjes Integration by Parts]
\label{thm:rs-integration-by-parts}
If \(f\) and \(\alpha\) are such that one of
\(\int_a^b f\,d\alpha\) and \(\int_a^b \alpha\,df\) exists, then the other
exists under the same Riemann--Stieltjes convention, and
\[
  \int_a^b f\,d\alpha+\int_a^b \alpha\,df
  =
  f(b)\alpha(b)-f(a)\alpha(a).
\]
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Smooth Integrator Reduction)}
\begin{theorem}[Reduction to Riemann Integration for a \(C^1\) Integrator]
\label{thm:rs-c1-reduction}
If \(\alpha\in C^1([a,b])\) and \(f\) is Riemann-integrable on \([a,b]\), then
\[
  \int_a^b f\,d\alpha=\int_a^b f(x)\alpha'(x)\,dx .
\]
\end{theorem}
\end{theorembox}

\begin{theorembox}{Theorem (Step Integrator)}
\begin{theorem}[Step Integrators Give Finite Sums]
\label{thm:rs-step-integrator-finite-sum}
If \(\alpha\) is constant except for finitely many jumps at points \(c_k\) and
\(f\) is continuous at each \(c_k\), then
\[
  \int_a^b f\,d\alpha=\sum_k f(c_k)\,\Delta\alpha(c_k).
\]
\end{theorem}
\end{theorembox}

\begin{remark*}[Proof idea]
The Cauchy common-refinement argument runs again. Uniform continuity makes
\(\omega_f(I)\) small on short slabs, and bounded variation controls
\(\sum_i|\Delta\alpha_i|\). The error has the form
\[
  \sum_i \omega_f(I_i)\,|\Delta\alpha_i|,
\]
so small oscillation multiplied by finite total variation is small.
\end{remark*}

\begin{remark*}[Sums as integrals]
If \(\alpha\) is a step function with jumps at points \(c_k\), then the
Stieltjes integral collapses to a weighted sum of the values \(f(c_k)\) times
the jumps. This is the conceptual doorway to probability: a cumulative
distribution function is an integrator, and expectation is an integral against
that integrator.
\end{remark*}

\begin{remark*}[Step integrator calculation]
Suppose \(\alpha\) is constant except for finitely many jumps
\(\Delta\alpha(c_k)=\alpha(c_k+)-\alpha(c_k-)\). Any sufficiently fine
partition has one tiny slab around each \(c_k\) carrying that jump, while all
other slabs have \(\Delta\alpha_i=0\). If \(f\) is continuous at each \(c_k\),
then the tagged height on the \(k\)-th jump slab is forced toward \(f(c_k)\),
so
\[
  \int_a^b f\,d\alpha=\sum_k f(c_k)\,\Delta\alpha(c_k).
\]
This is why a finite weighted sum is not a different species from an integral:
it is a Stieltjes integral against a discrete ruler.
\end{remark*}

\begin{remark*}[Shared-jump failure]
The new pathology is real. On \([0,1]\), let \(c=1/2\), let
\[
  \alpha(x)=\mathbf 1_{[c,1]}(x),
  \qquad
  f(x)=\mathbf 1_{[c,1]}(x).
\]
The only nonzero \(\Delta\alpha_i\) occurs on the slab containing \(c\). If the
tag for that slab is chosen left of \(c\), its contribution is \(0\); if the
tag is chosen at or right of \(c\), its contribution is \(1\). This discrepancy
does not shrink with the slab width, because the ruler has a whole unit of
mass concentrated at the jump. Tag independence fails, so the
Riemann--Stieltjes integral does not exist in this convention.
\end{remark*}

\begin{remark*}[Bug report]
Stieltjes is a sideways generalization, not the Lebesgue fix. Shared
discontinuities of \(f\) and \(\alpha\) can destroy tag independence, and the
standard existence theorem leans on the finite ruler budget
\(V_a^b(\alpha)<\infty\). Brownian paths have infinite variation almost surely,
so stochastic integration cannot be ordinary pathwise Riemann--Stieltjes
integration.
\end{remark*}

\begin{remark*}[Patch request]
The next stochastic patch is not ``make Stieltjes a little better.'' Brownian
motion forces a different limiting mode: an \(L^2\) or probabilistic limit
rather than a pathwise Riemann--Stieltjes limit. That is the structural reason
Ito integration is not just Stieltjes integration with a rougher integrator.
\end{remark*}
