\newpage
\phantomsection
\label{prf:preservation-of-intervals}

\begin{remark*}[Return]
\hyperref[thm:preservation-of-intervals]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Preservation of Intervals]
Let $I \subseteq \mathbb{R}$ be an interval and let $f : I \to \mathbb{R}$ be continuous on $I$. Then $f(I)$ is an interval.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
By the Characterization of Intervals, it suffices to show that $f(I)$ is closed under betweenness: for any $y_1, y_2 \in f(I)$ with $y_1 < y_2$, every $k$ satisfying $y_1 < k < y_2$ belongs to $f(I)$.

Let $y_1, y_2 \in f(I)$ with $y_1 < y_2$. By definition of the image, there exist $x_1, x_2 \in I$ with $f(x_1) = y_1$ and $f(x_2) = y_2$. Since $I$ is an interval, the subinterval $J := [\min(x_1, x_2), \max(x_1, x_2)] \subseteq I$. The function $f$ is continuous on $J$ as the restriction of a continuous function. Since $f(x_1) = y_1 < k < y_2 = f(x_2)$, the Intermediate Value Theorem applied to $f$ on $J$ produces $c \in J$ with $f(c) = k$. Since $J \subseteq I$, we have $c \in I$, so $k = f(c) \in f(I)$. Therefore $f(I)$ is closed under betweenness and is an interval.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Establish the strategy using interval characterization.
By the Characterization of Intervals, to prove $f(I)$ is an interval, it suffices to show that $f(I)$ is closed under betweenness. This means for any $y_1, y_2 \in f(I)$ with $y_1 < y_2$, every $k$ satisfying $y_1 < k < y_2$ must belong to $f(I)$.

\textbf{Step 2.} Set up the betweenness verification.
Let $y_1, y_2 \in f(I)$ with $y_1 < y_2$, and let $k$ satisfy $y_1 < k < y_2$. Since $y_1, y_2 \in f(I)$, by definition of the image there exist $x_1, x_2 \in I$ such that $f(x_1) = y_1$ and $f(x_2) = y_2$.

\textbf{Step 3.} Construct the connecting subinterval.
Since $I$ is an interval, it contains all points between any two of its elements. Therefore the closed interval $J := [\min(x_1, x_2), \max(x_1, x_2)] \subseteq I$. This construction handles both cases: whether $x_1 < x_2$ or $x_2 < x_1$.

\textbf{Step 4.} Apply the Intermediate Value Theorem.
The function $f$ is continuous on $J$ as the restriction of a continuous function to a subset of its domain. Since $f(x_1) = y_1 < k < y_2 = f(x_2)$, the values $f(x_1)$ and $f(x_2)$ bracket the target value $k$. By the Intermediate Value Theorem applied to the continuous function $f$ on the interval $J$, there exists $c \in J$ such that $f(c) = k$.

\textbf{Step 5.} Conclude that the intermediate value lies in the image.
Since $J \subseteq I$ and $c \in J$, we have $c \in I$. Therefore $k = f(c) \in f(I)$. Since $y_1, y_2 \in f(I)$ and $k$ were arbitrary, $f(I)$ is closed under betweenness and is therefore an interval.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof that verifies the interval characterization. The strategy involves pulling back two points in $f(I)$ to their preimages in $I$, using the interval structure of $I$ to construct a connecting subinterval, then applying the Intermediate Value Theorem to fill in every intermediate value. The argument works for any type of interval because it relies only on the Intermediate Value Theorem, not the Extreme Value Theorem.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:interval]{Definition of Interval}
  \item \hyperref[thm:characterization-of-intervals]{Characterization of Intervals}
  \item \hyperref[thm:bolzano-intermediate-value]{Bolzano's Intermediate Value Theorem}
  \item \hyperref[def:continuous-function]{Definition of Continuous Function}
\end{itemize}
\end{remark*}
