\newpage
\phantomsection
\label{prf:algebra-of-continuity-on-a-set}

\begin{remark*}[Return]
\hyperref[thm:algebra-of-continuity-on-a-set]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Algebra of Continuity on a Set]
Let $A \subseteq \mathbb{R}$, let $f,g : A \to \mathbb{R}$, and let $b \in \mathbb{R}$. If $f$ and $g$ are continuous on $A$, then $f+g$, $f-g$, $fg$, $bf$ are continuous on $A$, and $f/g$ is continuous on $\{x \in A : g(x) \neq 0\}$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $A \subseteq \mathbb{R}$, let $f,g : A \to \mathbb{R}$, and let $b \in \mathbb{R}$. Assume $f$ and $g$ are continuous on $A$. Let $c \in A$ be arbitrary. Since $f$ and $g$ are continuous on $A$, they are continuous at $c$. By the algebra of continuity at a point, the functions $f+g$, $f-g$, $fg$, and $bf$ are continuous at $c$. Since $c \in A$ was arbitrary, these functions are continuous on $A$.

For the quotient case, let $B = \{x \in A : g(x) \neq 0\}$. Let $c \in B$ be arbitrary. Then $f$ and $g$ are continuous at $c$ and $g(c) \neq 0$. By the algebra of continuity at a point, $f/g$ is continuous at $c$. Since $c \in B$ was arbitrary, $f/g$ is continuous on $B$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Establish the setup and reduction strategy.

Let $A \subseteq \mathbb{R}$, let $f,g : A \to \mathbb{R}$, and let $b \in \mathbb{R}$. Assume $f$ and $g$ are continuous on $A$. The strategy reduces global continuity on a set to pointwise continuity by fixing an arbitrary point and applying the algebra of continuity at a point.

\textbf{Step 2.} Prove continuity of $f+g$, $f-g$, $fg$, and $bf$ on $A$.

Let $c \in A$ be arbitrary. Since $f$ and $g$ are continuous on $A$, by definition they are continuous at every point of $A$, hence continuous at $c$. By the algebra of continuity at a point, the functions $f+g$, $f-g$, $fg$, and $bf$ are all continuous at $c$. Since $c \in A$ was arbitrary, these functions are continuous at every point of $A$, hence continuous on $A$.

\textbf{Step 3.} Prove continuity of $f/g$ on the appropriate domain.

Define $B = \{x \in A : g(x) \neq 0\}$. Let $c \in B$ be arbitrary. Then $c \in A$ and $g(c) \neq 0$. Since $f$ and $g$ are continuous on $A$, they are continuous at $c$. By the algebra of continuity at a point, since $g(c) \neq 0$, the quotient $f/g$ is continuous at $c$. Since $c \in B$ was arbitrary, $f/g$ is continuous on $B$.
\end{proof}

\begin{remark*}[Proof structure]
The proof uses a pointwise reduction strategy. Global continuity on a set is equivalent to continuity at every point of the set. The proof fixes an arbitrary point in the domain, applies the algebra of continuity at a point theorem, then discharges the arbitrariness to conclude global continuity. This reduction pattern is standard for translating pointwise properties to global properties on sets.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:continuous-on-a-set]{Definition of continuity on a set}
  \item \hyperref[def:continuous-at-a-point]{Definition of continuity at a point}
  \item \hyperref[thm:algebra-of-continuity-at-a-point]{Algebra of Continuity at a Point}
\end{itemize}
\end{remark*}
