\newpage
\phantomsection
\label{prf:monotone-discontinuities-countable}

\begin{remark*}[Return]
\hyperref[thm:monotone-discontinuities-countable]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Discontinuities of a Monotone Function Are Countable]
Let $f : I \to \mathbb{R}$ be a monotone function on an interval $I$. Then the set of discontinuities of $f$ is at most countable.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $D = \{c \in I : f \text{ is discontinuous at } c\}$. Without loss of generality, assume $f$ is monotone increasing. For each $c \in D$, the jump interval $J_c(f) = (f(c^{-}), f(c^{+}))$ is non-empty by the first kind nature of monotone discontinuities. By density of $\mathbb{Q}$ in $\mathbb{R}$, choose $r(c) \in J_c(f) \cap \mathbb{Q}$. Since jump intervals of distinct discontinuities are disjoint, the function $r : D \to \mathbb{Q}$ is injective. Therefore $D$ injects into the countable set $\mathbb{Q}$, hence $D$ is at most countable.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Define the discontinuity set and reduce to the increasing case. Let $D = \{c \in I : f \text{ is discontinuous at } c\}$. Without loss of generality, assume $f$ is monotone increasing; if $f$ is decreasing, apply the result to $-f$ and observe that $f$ is discontinuous at $c$ if and only if $-f$ is discontinuous at $c$.

\textbf{Step 2.} Construct jump intervals and select rational witnesses. For each discontinuity $c \in D$, the jump interval $J_c(f) = (f(c^{-}), f(c^{+}))$ is a non-empty open interval since monotone functions have only first kind discontinuities. By density of $\mathbb{Q}$ in $\mathbb{R}$, there exists a rational number $r(c) \in J_c(f)$ with $f(c^{-}) < r(c) < f(c^{+})$.

\textbf{Step 3.} Establish injectivity of the rational assignment. The function $r : D \to \mathbb{Q}$ defined by $c \mapsto r(c)$ is injective. To see this, let $c, d \in D$ with $c \neq d$. Then the jump intervals $J_c(f)$ and $J_d(f)$ are disjoint. Since $r(c) \in J_c(f)$ and $r(d) \in J_d(f)$, it follows that $r(c) \neq r(d)$.

\textbf{Step 4.} Conclude countability from the injection. The injection $r : D \hookrightarrow \mathbb{Q}$ into the countable set $\mathbb{Q}$ implies that $D$ is at most countable.
\end{proof}

\begin{remark*}[Proof structure]
This is a counting argument via injection into a countable set. The strategy exploits the geometric structure of monotone discontinuities: each discontinuity creates a non-empty "gap" (jump interval), and these gaps are disjoint. Density of rationals allows selection of distinct rational witnesses from each gap, creating an injection into $\mathbb{Q}$.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[prop:monotone-discontinuities-first-kind]{Discontinuities of a Monotone Function Are of the First Kind}
  \item \hyperref[cor:jump-intervals-for-monotone-discontinuities]{Jump Intervals of a Monotone Function Are Disjoint}
  \item \hyperref[thm:density-of-rationals]{Density of $\mathbb{Q}$ in $\mathbb{R}$}
  \item \hyperref[thm:countable-injection]{Injection into a Countable Set Is Countable}
\end{itemize}
\end{remark*}
