\newpage
\phantomsection
\label{prf:uniform-continuity-cauchy}

\begin{remark*}[Return]
\hyperref[prop:uniform-continuity-cauchy]{Return to Proposition}
\end{remark*}

\begin{theorem*}[Uniform Continuity Preserves Cauchy Sequences]
If $f \colon S \to \mathbb{R}$ is uniformly continuous and $(x_{n})$ is a Cauchy sequence in $S$, then $(f(x_{n}))$ is a Cauchy sequence in $\mathbb{R}$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $\varepsilon > 0$ be given. By uniform continuity of $f$ on $S$, there exists $\delta > 0$ such that for all $x, y \in S$ with $|x - y| < \delta$, one has $|f(x) - f(y)| < \varepsilon$. Since $(x_{n})$ is Cauchy, there exists $N \in \mathbb{N}$ such that for all $m, n \geq N$, one has $|x_{m} - x_{n}| < \delta$. For such $m, n$, uniform continuity yields $|f(x_{m}) - f(x_{n})| < \varepsilon$. Since $\varepsilon > 0$ was arbitrary, $(f(x_{n}))$ is Cauchy.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Apply uniform continuity to convert the target tolerance into a domain distance constraint. Given $\varepsilon > 0$, uniform continuity of $f$ on $S$ provides $\delta > 0$ such that whenever $x, y \in S$ satisfy $|x - y| < \delta$, the image points satisfy $|f(x) - f(y)| < \varepsilon$. This establishes the connection between domain proximity and image proximity at the required tolerance level.

\textbf{Step 2.} Apply the Cauchy property to achieve the domain distance constraint. Since $(x_{n})$ is Cauchy in $S$, the distance $\delta$ from Step 1 determines an index $N \in \mathbb{N}$ such that for all indices $m, n \geq N$, the sequence terms satisfy $|x_{m} - x_{n}| < \delta$. This achieves the domain proximity required by uniform continuity.

\textbf{Step 3.} Combine the constraints to establish the Cauchy property for the image sequence. For indices $m, n \geq N$, the domain points $x_{m}, x_{n} \in S$ satisfy $|x_{m} - x_{n}| < \delta$, so uniform continuity from Step 1 yields $|f(x_{m}) - f(x_{n})| < \varepsilon$. Since $\varepsilon > 0$ was arbitrary, the sequence $(f(x_{n}))$ satisfies the definition of Cauchy.
\end{proof}

\begin{remark*}[Proof structure]
Direct proof using the definition of Cauchy sequences. The strategy chains uniform continuity with the Cauchy property through an intermediate tolerance $\delta$: uniform continuity converts the target tolerance $\varepsilon$ into a domain constraint $\delta$, while the Cauchy hypothesis provides eventual satisfaction of this domain constraint. The $\delta$ serves as a bridge connecting the two conditions rather than an independent parameter.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:uniform-continuity]{Definition of Uniform Continuity}
  \item \hyperref[def:cauchy-sequence]{Definition of Cauchy Sequence}
\end{itemize}
\end{remark*}
