\newpage
\phantomsection
\label{prf:discontinuity-on-set}

\begin{remark*}[Return]
\hyperref[prop:discontinuity-on-set]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Discontinuity on a Set Is Failure at a Point]
Let $A \subseteq \mathbb{R}$ and let $f : A \to \mathbb{R}$. Then $f$ is discontinuous on $A$ if and only if there exists at least one point $c \in A$ at which $f$ is discontinuous.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
By definition, $f$ is continuous on $A$ if and only if $f$ is continuous at every point $c \in A$. Discontinuity on $A$ is the negation of this statement.

$(\Rightarrow)$ Suppose $f$ is discontinuous on $A$. Then $f$ is not continuous on $A$, meaning the universal statement $\forall c \in A,\ f \text{ is continuous at } c$ is false. By negation of the universal quantifier, there exists $c \in A$ such that $f$ is not continuous at $c$. Hence $f$ is discontinuous at $c$.

$(\Leftarrow)$ Suppose there exists $c \in A$ at which $f$ is discontinuous. Then $f$ fails to be continuous at this particular point of $A$, so $f$ is not continuous at every point of $A$. Therefore $f$ is not continuous on $A$, i.e., $f$ is discontinuous on $A$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Establish the logical framework. By definition, $f$ is continuous on $A$ if and only if $f$ is continuous at every point $c \in A$. This is a universal quantification: $\forall c \in A,\ f \text{ is continuous at } c$. Discontinuity on $A$ is precisely the negation of continuity on $A$, so it is the negation of this universal statement.

\textbf{Step 2.} Prove the forward direction $(\Rightarrow)$. Assume $f$ is discontinuous on $A$. Then $f$ is not continuous on $A$, which means the universal statement $\forall c \in A,\ f \text{ is continuous at } c$ is false. By the logical principle that $\lnot\,\forall x\,P(x) \iff \exists x\,\lnot P(x)$, there exists at least one point $c \in A$ such that $f$ is not continuous at $c$. This means $f$ is discontinuous at $c$.

\textbf{Step 3.} Prove the reverse direction $(\Leftarrow)$. Assume there exists $c \in A$ at which $f$ is discontinuous. Then $f$ fails to be continuous at this particular point of $A$. Since continuity on $A$ requires continuity at every point of $A$, the failure at even one point means $f$ is not continuous at every point of $A$. Therefore $f$ is not continuous on $A$, which by definition means $f$ is discontinuous on $A$.
\end{proof}

\begin{remark*}[Proof structure]
Pure quantifier logic in both directions. Continuity on $A$ is a universal statement over $A$; discontinuity on $A$ is its negation. The forward direction unpacks the negation of a universal quantifier using the logical equivalence $\lnot\,\forall x\,P(x) \iff \exists x\,\lnot P(x)$. The reverse direction exploits the fact that one witness of failure destroys the universal requirement. No $\varepsilon$-$\delta$ construction is needed beyond invoking the definitions.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:continuity-on-set]{Definition of continuity on a set}
  \item \hyperref[def:continuous-at-point]{Definition of continuity at a point}
  \item \hyperref[def:discontinuity-at-point]{Definition of discontinuity at a point}
\end{itemize}
\end{remark*}
