\newpage
\phantomsection
\label{prf:exponentiation-continuous-base}

\begin{remark*}[Return]
\hyperref[thm:exponentiation-continuous-base]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Exponentiation Is Continuous, I]
Let $a > 0$ be a positive real number. Then the function $f \colon \mathbb{R} \to \mathbb{R}$ defined by
\[
f(x) := a^x
\]
is continuous.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $c \in \mathbb{R}$ be arbitrary. Since $a^x = e^{x \ln a}$ for all $x \in \mathbb{R}$, the function $f(x) = a^x$ is the composition of the continuous function $g(x) = x \ln a$ and the exponential function $h(y) = e^y$. Since the composition of continuous functions is continuous, $f$ is continuous at $c$. Since $c$ was arbitrary, $f$ is continuous on $\mathbb{R}$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Express $a^x$ using the natural exponential function. For any positive real number $a$ and any real number $x$, we have $a^x = e^{x \ln a}$. This identity holds because $e^{\ln a} = a$, so raising both sides to the power $x$ gives $(e^{\ln a})^x = a^x$, which equals $e^{x \ln a}$ by the power rule for exponentials.

\textbf{Step 2.} Identify the component functions. The function $f(x) = a^x = e^{x \ln a}$ can be written as the composition $(h \circ g)(x)$ where $g(x) = x \ln a$ and $h(y) = e^y$.

\textbf{Step 3.} Verify continuity of component functions. The function $g(x) = x \ln a$ is a linear function with slope $\ln a$, hence continuous on $\mathbb{R}$. The exponential function $h(y) = e^y$ is continuous on $\mathbb{R}$ by the fundamental properties of the exponential function.

\textbf{Step 4.} Apply composition theorem. Since both $g$ and $h$ are continuous on $\mathbb{R}$, their composition $f = h \circ g$ is continuous on $\mathbb{R}$ by the theorem that the composition of continuous functions is continuous.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof using function composition. The key insight is to express the exponential function with arbitrary base in terms of the natural exponential function, which has well-established continuity properties. The proof reduces the problem to applying the fundamental theorem about continuity of function compositions.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:continuity]{Definition of Continuity}
  \item \hyperref[def:exponential-function]{Definition of Exponential Function}
  \item \hyperref[thm:exponential-continuous]{Continuity of Natural Exponential Function}
  \item \hyperref[thm:composition-continuous]{Continuity of Function Composition}
  \item \hyperref[thm:linear-continuous]{Continuity of Linear Functions}
\end{itemize}
\end{remark*}
