\newpage
\phantomsection
\label{prf:polynomials-are-continuous}

\begin{remark*}[Return]
\hyperref[thm:polynomials-are-continuous]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Any Real Polynomial Is a Continuous Function]
Let
\[
  P(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_n x^n
\]
be a real polynomial. Then $P$ is a continuous function.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Write $P(x) = T_0 + T_1 + \cdots + T_n$ where $T_k = a_k x^k$ for $k = 0, 1, \ldots, n$. Each term $T_k$ is continuous: $T_0 = a_0$ is constant hence continuous; for $k \geq 1$, if $a_k = 1$ then $T_k = x^k$ is continuous by the power function theorem, and if $a_k \neq 1$ then $T_k = a_k \cdot x^k$ is continuous by the constant multiple rule. Since $P$ is a finite sum of continuous functions, $P$ is continuous by the sum rule.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Decompose the polynomial into individual terms.
Write $P(x) = T_0 + T_1 + \cdots + T_n$ where $T_k = a_k x^k$ for $k = 0, 1, \ldots, n$. This separates the polynomial into components that can be analyzed individually for continuity.

\textbf{Step 2.} Establish continuity of each term by cases.
For the constant term: $T_0 = a_0$ is a constant function, hence continuous.
For monomial terms when $k \geq 1$: If $a_k = 1$, then $T_k = x^k$ is a power function, hence continuous. If $a_k \neq 1$, then $T_k = a_k \cdot x^k$ is a scalar multiple of the continuous function $x^k$, hence continuous by the constant multiple rule.

\textbf{Step 3.} Apply the sum rule to conclude.
Since each term $T_k$ is continuous and $P$ is a finite sum of these continuous functions, $P$ is continuous by the sum rule for continuous functions.
\end{proof}

\begin{remark*}[Proof structure]
The proof uses a direct approach by decomposing the polynomial into terms and establishing continuity term by term. Each term is classified as either a constant function, a power function, or a constant multiple of a power function, allowing application of the appropriate continuity theorem. The finite sum rule then combines these results to establish continuity of the entire polynomial.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[lem:power-function-continuous]{Power Function Is Continuous}
  \item \hyperref[thm:constant-multiple-rule-continuous]{Constant Multiple Rule for Continuous Functions}
  \item \hyperref[thm:sum-rule-continuous-functions]{Sum Rule for Continuous Functions}
\end{itemize}
\end{remark*}
