\newpage
\phantomsection
\label{prf:inverse-strictly-monotone}

\begin{remark*}[Return]
\hyperref[prop:inverse-strictly-monotone]{Return to Proposition}
\end{remark*}

\begin{theorem*}[Inverse of a Strictly Monotone Function]
Let $f : I \to \mathbb{R}$ be strictly monotone on an interval $I$. Then $f$ is injective, its inverse $f^{-1} : f(I) \to I$ exists, and $f^{-1}$ is strictly monotone in the same direction as $f$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Without loss of generality assume $f$ is strictly increasing. For injectivity, if $x, y \in I$ with $x \neq y$, then either $x < y$ or $y < x$, so strict monotonicity gives either $f(x) < f(y)$ or $f(y) < f(x)$, hence $f(x) \neq f(y)$. Since $f$ is injective, the inverse $f^{-1} : f(I) \to I$ exists with $f^{-1}(f(x)) = x$ for all $x \in I$. For strict monotonicity of $f^{-1}$, if $u, v \in f(I)$ with $u < v$, then $u = f(x)$ and $v = f(y)$ for some $x, y \in I$. Since $f(x) < f(y)$ and $f$ is strictly increasing, $x < y$. Therefore $f^{-1}(u) = x < y = f^{-1}(v)$, so $f^{-1}$ is strictly increasing.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Establish injectivity of $f$.
Without loss of generality assume $f$ is strictly increasing. Let $x, y \in I$ with $x \neq y$. Since the real numbers are totally ordered, either $x < y$ or $y < x$. If $x < y$, then strict monotonicity gives $f(x) < f(y)$, so $f(x) \neq f(y)$. If $y < x$, then strict monotonicity gives $f(y) < f(x)$, so again $f(x) \neq f(y)$. Therefore $x \neq y$ implies $f(x) \neq f(y)$, proving $f$ is injective.

\textbf{Step 2.} Establish existence of the inverse function.
Since $f$ is injective, for each $y \in f(I)$ there exists a unique $x \in I$ such that $f(x) = y$. This defines the inverse function $f^{-1} : f(I) \to I$ by $f^{-1}(y) = x$ where $f(x) = y$. By definition of inverse functions, $f^{-1}(f(x)) = x$ for all $x \in I$ and $f(f^{-1}(y)) = y$ for all $y \in f(I)$.

\textbf{Step 3.} Prove $f^{-1}$ is strictly monotone in the same direction.
Let $u, v \in f(I)$ with $u < v$. Since $u, v \in f(I)$, there exist $x, y \in I$ such that $f(x) = u$ and $f(y) = v$. Thus $f(x) < f(y)$. Since $f$ is strictly increasing and $f(x) < f(y)$, the contrapositive of strict monotonicity ensures $x < y$ (if $x \geq y$, then $f(x) \geq f(y)$, contradicting $f(x) < f(y)$). Therefore $f^{-1}(u) = x < y = f^{-1}(v)$, proving $f^{-1}$ is strictly increasing.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof that unfolds the logical implications of strict monotonicity. The key insight is that strict monotonicity forces distinct inputs to produce distinct outputs, which is precisely the condition for injectivity and hence existence of an inverse. The inverse inherits strict monotonicity because the ordering relationships are preserved through the inverse correspondence: if $f$ maps smaller inputs to smaller outputs, then $f^{-1}$ maps smaller outputs back to smaller inputs.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:strictly-monotone]{Definition of strictly monotone function}
  \item \hyperref[def:inverse-function]{Definition of inverse function}
\end{itemize}
\end{remark*}
