\newpage
\phantomsection
\label{prf:monotone-continuous-on-dense-set}

\begin{remark*}[Return]
\hyperref[cor:monotone-continuous-on-dense-set]{Return to Corollary}
\end{remark*}

\begin{theorem*}[Monotone Function Is Continuous on a Dense Set]
Let $f : I \to \mathbb{R}$ be a monotone function on an interval $I$. Then the set of points of continuity of $f$ is dense in $I$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $D = \{x \in I : f \text{ is not continuous at } x\}$ be the set of discontinuities. By the theorem that discontinuities of a monotone function are countable, $D$ is at most countable. The set of points of continuity is $I \setminus D$. To show $I \setminus D$ is dense in $I$, let $(a, b) \subseteq I$ be any open subinterval with $a < b$. Since $(a, b)$ is uncountable while $D$ is at most countable, $(a, b) \not\subseteq D$. Therefore there exists $x \in (a, b)$ with $x \notin D$, so $(a, b) \cap (I \setminus D) \neq \emptyset$. Since every open subinterval of $I$ meets $I \setminus D$, the set $I \setminus D$ is dense in $I$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Define the set of discontinuities $D = \{x \in I : f \text{ is not continuous at } x\}$. By the theorem on discontinuities of monotone functions, $D$ is at most countable. This gives us precise control over the size of the set where $f$ fails to be continuous.

\textbf{Step 2.} The set of continuity points is $I \setminus D$. To prove this is dense in $I$, consider any open subinterval $(a, b) \subseteq I$ with $a < b$. The interval $(a, b)$ has uncountably many points, while $D$ has at most countably many points.

\textbf{Step 3.} Since an uncountable set cannot be contained in a countable set, $(a, b) \not\subseteq D$. Therefore there exists at least one point $x \in (a, b)$ such that $x \notin D$, which means $x$ is a point of continuity and $(a, b) \cap (I \setminus D) \neq \emptyset$.

\textbf{Step 4.} Since every open subinterval of $I$ contains a point from $I \setminus D$, the set $I \setminus D$ is dense in $I$ by definition.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof using a cardinality argument. The strategy exploits the fact that discontinuities form a countable set while open intervals are uncountable, creating an inevitable overlap between any open interval and the complement of the discontinuity set. The key insight is translating the countability constraint into a density conclusion through the intermediate step of examining open subintervals.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[thm:monotone-discontinuities-countable]{Discontinuities of a Monotone Function Are Countable}
  \item \hyperref[thm:intervals-are-uncountable]{Intervals of $\mathbb{R}$ Are Uncountable}
  \item \hyperref[def:dense]{Definition of Dense Subset}
\end{itemize}
\end{remark*}
