\newpage
\phantomsection
\label{prf:local-properties-of-continuous-functions}

\begin{remark*}[Return]
\hyperref[thm:local-properties-of-continuous-functions]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Local Properties of Continuous Functions]
Let $f : I \to \mathbb{R}$ be continuous at $c \in I$. Then:
\begin{enumerate}[(1)]
\item There exist $\delta > 0$ and $M > 0$ such that $|f(x)| \leq M$ for all $x \in I$ with $|x - c| < \delta$.
\item If $f(c) \neq 0$, there exist $\delta > 0$ and $\alpha > 0$ such that $|f(x)| \geq \alpha$ for all $x \in I$ with $|x - c| < \delta$.
\item If $f(c) > 0$, there exists $\delta > 0$ such that $f(x) > 0$ for all $x \in I$ with $|x - c| < \delta$. If $f(c) < 0$, there exists $\delta > 0$ such that $f(x) < 0$ for all $x \in I$ with $|x - c| < \delta$.
\end{enumerate}
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Since $f$ is continuous at $c$, the definition of continuity gives $\lim_{x \to c} f(x) = f(c)$.

For part (1), apply the Limit Implies Local Bounding theorem to $\lim_{x \to c} f(x) = f(c)$, which supplies $\delta > 0$ and $M > 0$ such that $|f(x)| \leq M$ for all $x \in I$ with $|x - c| < \delta$.

For part (2), since $f(c) \neq 0$, apply the Limits Bounded Away from Zero theorem to $\lim_{x \to c} f(x) = f(c)$, which supplies $\delta > 0$ and $\alpha > 0$ such that $|f(x)| \geq \alpha$ for all $x \in I$ with $|x - c| < \delta$.

For part (3), apply Sign Preservation to $f$ at $c$, which supplies $\delta > 0$ such that $f(x) > 0$ for all $x \in I$ with $|x - c| < \delta$ when $f(c) > 0$, and $f(x) < 0$ for all $x \in I$ with $|x - c| < \delta$ when $f(c) < 0$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Establish the fundamental connection between continuity and limits. Since $f$ is continuous at $c$, the definition of continuity at a point gives $\lim_{x \to c} f(x) = f(c)$. This limit relationship is the key to all three local properties, as each follows from applying established limit theorems to this convergence.

\textbf{Step 2.} Prove local boundedness. Apply the Limit Implies Local Bounding theorem to the limit $\lim_{x \to c} f(x) = f(c)$. This theorem guarantees the existence of $\delta > 0$ and $M > 0$ such that $|f(x)| \leq M$ for all $x \in I$ with $|x - c| < \delta$. The function is therefore bounded in a neighborhood of $c$.

\textbf{Step 3.} Prove bounded away from zero when $f(c) \neq 0$. Since $f(c) \neq 0$, apply the Limits Bounded Away from Zero theorem to $\lim_{x \to c} f(x) = f(c)$. This theorem provides $\delta > 0$ and $\alpha > 0$ such that $|f(x)| \geq \alpha$ for all $x \in I$ with $|x - c| < \delta$. The function avoids zero in a neighborhood of $c$ because the limit is nonzero.

\textbf{Step 4.} Prove sign preservation. Apply the Sign Preservation theorem to $f$ at $c$. When $f(c) > 0$, this theorem supplies $\delta > 0$ such that $f(x) > 0$ for all $x \in I$ with $|x - c| < \delta$. When $f(c) < 0$, it supplies $\delta > 0$ such that $f(x) < 0$ for all $x \in I$ with $|x - c| < \delta$. The function preserves the sign of $f(c)$ in a neighborhood of $c$.
\end{proof}

\begin{remark*}[Proof structure]
The proof uses direct application of established limit theorems. Each part is a two-step reduction: continuity at $c$ gives the limit relation $\lim_{x \to c} f(x) = f(c)$, then the appropriate Chapter 3 limit theorem delivers the desired local property immediately. The strategy demonstrates how local properties of continuous functions derive naturally from the corresponding properties of limits.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:continuous-at-point]{Definition of continuity at a point}
  \item \hyperref[thm:limit-implies-local-bounding]{Limit Implies Local Bounding}
  \item \hyperref[thm:limit-quotient]{Limits Bounded Away from Zero}
  \item \hyperref[prop:sign-preservation]{Sign Preservation}
\end{itemize}
\end{remark*}
