\newpage
\phantomsection
\label{prf:darboux-property}

\begin{remark*}[Return]
\hyperref[thm:darboux-property]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Darboux Property]
Let $f : [a, b] \to \mathbb{R}$ be continuous on the closed interval $[a, b]$. For any $c \in \mathbb{R}$, if $f(x) \neq c$ for all $x \in [a, b]$, then either $f(x) > c$ for all $x \in [a, b]$, or $f(x) < c$ for all $x \in [a, b]$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $f$ be continuous on $[a, b]$ and define $S = \{f(x) \mid x \in [a, b]\}$. By the Extreme Value Theorem, $f$ attains its maximum and minimum on $[a, b]$, so $S = [\inf S, \sup S]$ by the Intermediate Value Theorem. Let $c \in \mathbb{R}$ with $f(x) \neq c$ for all $x \in [a, b]$. Then $c \notin S$. Since $S = [\inf S, \sup S]$ is an interval, either $c < \inf S$ or $c > \sup S$. If $c < \inf S$, then $f(x) \geq \inf S > c$ for all $x \in [a, b]$. If $c > \sup S$, then $f(x) \leq \sup S < c$ for all $x \in [a, b]$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Define the range of $f$ and establish its structure. Let $S = \{f(x) \mid x \in [a, b]\}$ be the range of $f$ on $[a, b]$. Since $f$ is continuous on the closed and bounded interval $[a, b]$, the Extreme Value Theorem guarantees that $f$ attains its maximum and minimum values on $[a, b]$. Therefore, $\inf S$ and $\sup S$ exist and are finite.

\textbf{Step 2.} Show that $S$ forms a closed interval. By the Intermediate Value Theorem, since $f$ is continuous on $[a, b]$, the range $S$ contains every value between $\inf S$ and $\sup S$. Therefore, $S = [\inf S, \sup S]$, which is a closed interval.

\textbf{Step 3.} Analyze the position of $c$ relative to $S$. Given that $f(x) \neq c$ for all $x \in [a, b]$, it follows that $c \notin S$. Since $S = [\inf S, \sup S]$ is an interval, the value $c$ cannot lie between $\inf S$ and $\sup S$. Therefore, either $c < \inf S$ or $c > \sup S$.

\textbf{Step 4.} Conclude the dichotomy. If $c < \inf S$, then for all $x \in [a, b]$, $f(x) \geq \inf S > c$, so $f(x) > c$. If $c > \sup S$, then for all $x \in [a, b]$, $f(x) \leq \sup S < c$, so $f(x) < c$. Thus, either $f(x) > c$ for all $x \in [a, b]$, or $f(x) < c$ for all $x \in [a, b]$.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof utilizing the topological properties of continuous functions. The key insight is that the range of a continuous function on a closed interval forms a closed interval itself, which means it has no gaps. When a value $c$ is excluded from this range, it must lie entirely outside the interval, creating the strict dichotomy between being above or below all function values.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[thm:extreme-value-theorem]{Extreme Value Theorem}
  \item \hyperref[thm:bolzano-intermediate-value]{Bolzano's Intermediate Value Theorem}
  \item \hyperref[def:continuous-function]{Definition of Continuous Function}
\end{itemize}
\end{remark*}
