\newpage
\phantomsection
\label{prf:lipschitz-implies-uniform-continuous}

\begin{remark*}[Return]
\hyperref[thm:lipschitz-implies-uniform-continuous]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Lipschitz Continuity Implies Uniform Continuity]
If $f \colon S \to \mathbb{R}$ is Lipschitz continuous, then $f$ is uniformly continuous on $S$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Since $f$ is Lipschitz continuous, there exists $K > 0$ such that $|f(x) - f(y)| \leq K|x - y|$ for all $x, y \in S$. Let $\varepsilon > 0$ be given. Set $\delta := \varepsilon / K > 0$. For any $x, y \in S$ with $|x - y| < \delta$, the Lipschitz condition yields $|f(x) - f(y)| \leq K|x - y| < K \cdot (\varepsilon/K) = \varepsilon$. Since $\delta$ depends only on $\varepsilon$ and $K$, the function $f$ is uniformly continuous on $S$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Extract the Lipschitz constant. Since $f$ is Lipschitz continuous on $S$, there exists a constant $K > 0$ such that $|f(x) - f(y)| \leq K|x - y|$ for all $x, y \in S$. This global bound controls the rate of change of $f$ everywhere on $S$.

\textbf{Step 2.} Construct the uniform modulus of continuity. Given $\varepsilon > 0$, set $\delta := \varepsilon / K$. Since both $\varepsilon > 0$ and $K > 0$, it follows that $\delta > 0$. This choice of $\delta$ is independent of any particular points in $S$.

\textbf{Step 3.} Verify the uniform continuity condition. For any $x, y \in S$ satisfying $|x - y| < \delta$, the Lipschitz condition gives
\[
|f(x) - f(y)| \leq K|x - y| < K \cdot \frac{\varepsilon}{K} = \varepsilon.
\]
The inequality chain closes exactly at $\varepsilon$, establishing that the same $\delta$ works uniformly for all pairs of points in $S$.

\textbf{Step 4.} Conclude uniform continuity. Since for every $\varepsilon > 0$ there exists $\delta > 0$ (namely $\delta = \varepsilon/K$) such that $|x - y| < \delta$ implies $|f(x) - f(y)| < \varepsilon$ for all $x, y \in S$, the function $f$ is uniformly continuous on $S$.
\end{proof}

\begin{remark*}[Proof structure]
Direct proof using the definition of uniform continuity. The Lipschitz bound provides immediate global control over output separation in terms of input separation. The choice $\delta = \varepsilon/K$ creates a direct inequality chain that closes at $\varepsilon$ without requiring compactness arguments or triangle inequality manipulations.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:lipschitz-continuous]{Definition of Lipschitz Continuity}
  \item \hyperref[def:uniform-continuous]{Definition of Uniform Continuity}
\end{itemize}
\end{remark*}
