\begin{definitionbox}{Definition (Convergence of a Sequence)}
% ---------------------------------------------------------
% Definition: Convergence of a Sequence
% Label: def:convergent-sequence
% ---------------------------------------------------------
\begin{definition}[Convergence of a Sequence]
\label{def:convergent-sequence}

Let $(x_n) \subseteq \mathbb{R}$. The sequence $(x_n)$ \textbf{converges}
to $L \in \mathbb{R}$ if
\[
    \forall \varepsilon > 0 \;\exists N \in \mathbb{N} \;\forall n \ge N
    \;\bigl(|x_n - L| < \varepsilon\bigr).
\]
The value $L$ is called the \textbf{limit} of $(x_n)$, written
$x_n \to L$ or $\displaystyle\lim_{n \to \infty} x_n = L$.
A sequence that converges to some $L \in \mathbb{R}$ is called
\textbf{convergent}; otherwise it is called \textbf{divergent}.
\end{definition}
\end{definitionbox}

\begin{remark*}[Standard quantified statement]
\[
\begin{aligned}
&\forall (x_n) \subseteq \mathbb{R} \;\forall L \in \mathbb{R}\\
&\quad\Bigl(
    x_n \to L
    \;\Longleftrightarrow\;
    \forall \varepsilon > 0 \;\exists N \in \mathbb{N} \;\forall n \ge N
    \;\bigl(|x_n - L| < \varepsilon\bigr)
\Bigr).
\end{aligned}
\]
\end{remark*}

\begin{remark*}[Definition predicate reading]
\[
\operatorname{ConvergentSequence}(x_n, L)
\;:=\;
\forall \varepsilon > 0 \;\exists N \in \mathbb{N} \;\forall n \ge N
\;\operatorname{OutputTolerance}(x_n, L, \varepsilon).
\]
\end{remark*}

\begin{remark*}[Negated quantified statement]
\[
\begin{aligned}
x_n \not\to L
\;\Longleftrightarrow\;
&\;\exists \varepsilon > 0 \;\forall N \in \mathbb{N} \;\exists n \ge N\\
&\quad\bigl(|x_n - L| \ge \varepsilon\bigr).
\end{aligned}
\]
\end{remark*}

\begin{remark*}[Negation predicate reading]
\[
\operatorname{NotConvergentTo}(x_n,L)
\;:=\;
\exists \varepsilon > 0 \;\forall N \in \mathbb{N} \;\exists n \ge N
\;\bigl(|x_n - L| \ge \varepsilon\bigr).
\]
\end{remark*}

\begin{remark*}[Failure modes]
Failure of convergence to a fixed $L$ means that some positive tolerance
cannot be controlled on any tail. The escaped terms may oscillate, drift
monotonically away, or grow without bound, but all such behavior is
captured by the same persistent-tolerance obstruction.
\end{remark*}

\begin{remark*}[Failure mode decomposition]
The negation decomposes into a single structural obstruction:
\[
\underbrace{\exists \varepsilon > 0}_{\text{a fixed tolerance}}
\;\underbrace{\forall N \in \mathbb{N}}_{\text{no tail suffices}}
\;\underbrace{\exists n \ge N}_{\text{terms escape infinitely often}}
\;\underbrace{|x_n - L| \ge \varepsilon}_{\text{outside the target interval}}.
\]
The sequence fails to converge to $L$ not by drifting away once, but
by returning outside the $\varepsilon$-interval infinitely often regardless
of how far along the tail one looks.
\end{remark*}

\begin{remark*}[Interpretation]
The quantifier order $\forall \varepsilon \;\exists N \;\forall n \ge N$
encodes a strict dependency: $N$ is permitted to depend on $\varepsilon$,
but not on $n$. This asymmetry is load-bearing. Reversing the outer
quantifiers to $\exists N \;\forall \varepsilon$ would assert that a
single index $N$ controls all tolerances simultaneously, which is a
strictly stronger and generally false condition. The condition
$|x_n - L| < \varepsilon$ is the membership assertion $x_n \in (L -
\varepsilon,\, L + \varepsilon)$; convergence is therefore the statement
that the tail of the sequence is eventually contained in every
$\varepsilon$-neighborhood of $L$.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:sequence]{Definition of sequence}
\end{itemize}
\end{dependencies}

\begin{definitionbox}{Definition (Convergence --- Neighborhood Formulation)}
% ---------------------------------------------------------
% Definition: Convergence --- Neighborhood Formulation
% Label: def:convergent-sequence-neighborhood
% ---------------------------------------------------------
\begin{definition}[Convergence --- Neighborhood Formulation]
\label{def:convergent-sequence-neighborhood}

Let $(x_n) \subseteq \mathbb{R}$ and let $L \in \mathbb{R}$. The sequence
$(x_n)$ \textbf{converges} to $L$ if for every $\varepsilon > 0$ the
$\varepsilon$-neighborhood
\[
    V_\varepsilon(L) \;:=\; (L - \varepsilon,\, L + \varepsilon)
\]
contains all but finitely many terms of $(x_n)$; that is,
\[
    \forall \varepsilon > 0 \;\exists N \in \mathbb{N} \;\forall n \ge N
    \;\bigl(x_n \in V_\varepsilon(L)\bigr).
\]
\end{definition}
\end{definitionbox}

\begin{remark*}[Standard quantified statement]
\[
\begin{aligned}
&\forall (x_n) \subseteq \mathbb{R} \;\forall L \in \mathbb{R}\\
&\quad\Bigl(
    x_n \to L
    \;\Longleftrightarrow\;
    \forall \varepsilon > 0 \;\exists N \in \mathbb{N} \;\forall n \ge N
    \;\bigl(x_n \in V_\varepsilon(L)\bigr)
\Bigr).
\end{aligned}
\]
\end{remark*}

\begin{remark*}[Definition predicate reading]
\[
\operatorname{ConvergentSequence}(x_n, L)
\;:=\;
\forall \varepsilon > 0 \;\exists N \in \mathbb{N} \;\forall n \ge N
\;\bigl(x_n \in V_\varepsilon(L)\bigr).
\]
\end{remark*}

\begin{remark*}[Negated quantified statement]
\[
\begin{aligned}
x_n \not\to L
\;\Longleftrightarrow\;
&\;\exists \varepsilon > 0 \;\forall N \in \mathbb{N} \;\exists n \ge N\\
&\quad\bigl(x_n \notin V_\varepsilon(L)\bigr).
\end{aligned}
\]
\end{remark*}

\begin{remark*}[Negation predicate reading]
\[
\operatorname{NotConvergentTo}(x_n,L)
\;:=\;
\exists \varepsilon > 0 \;\forall N \in \mathbb{N} \;\exists n \ge N
\;\bigl(x_n \notin V_\varepsilon(L)\bigr).
\]
\end{remark*}

\begin{remark*}[Failure modes]
Failure of the neighborhood formulation is exactly failure to trap a
tail in every neighborhood of $L$. Different examples may escape by
oscillation, by monotone drift, or by unbounded growth, but the formal
failure is always the existence of one neighborhood that every tail
misses at least once.
\end{remark*}

\begin{remark*}[Failure mode decomposition]
\[
\underbrace{\exists \varepsilon > 0}_{\text{a fixed neighborhood}}
\;\underbrace{\forall N \in \mathbb{N}}_{\text{no tail suffices}}
\;\underbrace{\exists n \ge N}_{\text{terms escape infinitely often}}
\;\underbrace{x_n \notin V_\varepsilon(L)}_{\text{outside every candidate neighborhood}}.
\]
The sequence fails to converge to $L$ precisely when some neighborhood
of $L$ contains only finitely many terms: infinitely many terms lie
permanently outside it.
\end{remark*}

\begin{remark*}[Interpretation]
The neighborhood formulation reframes convergence as a set-containment
condition rather than an inequality condition. The assertion $x_n \in
V_\varepsilon(L)$ is identical to $|x_n - L| < \varepsilon$; the two
definitions are logically equivalent and the choice between them is one
of language, not content. The neighborhood language is the natural
bridge to the topological formulation: in a general topological space,
open sets replace $\varepsilon$-neighborhoods and the definition reads
identically with $V_\varepsilon(L)$ replaced by any open set $U$
containing $L$. The phrase \emph{all but finitely many terms} is the
canonical prose compression of the quantifier block $\exists N \in
\mathbb{N} \;\forall n \ge N$, and is standard in the literature.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:convergent-sequence]{Convergence of a Sequence}
  \item \hyperref[def:epsilon-neighbourhood]{$\varepsilon$-neighbourhood}
\end{itemize}
\end{dependencies}










\begin{theorembox}{Theorem (Equivalence of Convergence Formulations)}
% ---------------------------------------------------------
% Theorem: Equivalence of Convergence Formulations
% Label: thm:equivalence-of-convergence-formulations
% ---------------------------------------------------------
\begin{theorem}[Equivalence of Convergence Formulations]
\label{thm:equivalence-of-convergence-formulations}

Let $(x_n) \subseteq \mathbb{R}$ and let $L \in \mathbb{R}$. The following
statements are equivalent.
\begin{enumerate}[label=\textup{(\alph*)}]
    \item $x_n \to L$.
    \item $\forall \varepsilon > 0 \;\exists K \in \mathbb{N} \;\forall n \ge K
          \;\bigl(|x_n - L| < \varepsilon\bigr)$.
    \item $\forall \varepsilon > 0 \;\exists K \in \mathbb{N} \;\forall n \ge K
          \;\bigl(L - \varepsilon < x_n < L + \varepsilon\bigr)$.
    \item $\forall \varepsilon > 0 \;\exists K \in \mathbb{N} \;\forall n \ge K
          \;\bigl(x_n \in V_\varepsilon(L)\bigr)$.
\end{enumerate}

\smallskip
\noindent
\hyperref[prf:equivalence-of-convergence-formulations]{\textit{Go to proof.}}
\end{theorem}
\end{theorembox}

\begin{remark*}[Standard quantified statement]
\[
\begin{aligned}
&\forall (x_n) \subseteq \mathbb{R} \;\forall L \in \mathbb{R}\\
&\quad\Bigl(
    (a) \;\Longleftrightarrow\; (b)
         \;\Longleftrightarrow\; (c)
         \;\Longleftrightarrow\; (d)
\Bigr).
\end{aligned}
\]
\end{remark*}

\begin{remark*}[Theorem predicate reading]
\[
\operatorname{EquivalentConvergenceForms}(x_n,L)
\;:=\;
\operatorname{ConvergentSequence}(x_n,L)
\Longleftrightarrow
\operatorname{NeighborhoodConvergentSequence}(x_n,L).
\]
\end{remark*}

\begin{remark*}[Interpretation]
The four conditions are the same geometric fact written in four
notational registers. Condition (a) is the informal assertion.
Condition (b) is the canonical $\varepsilon$-$K$ definition: the
absolute value formulation. Condition (c) makes the interval
structure explicit by expanding $|x_n - L| < \varepsilon$ into its
equivalent double inequality $L - \varepsilon < x_n < L +
\varepsilon$; this is useful in proofs where upper and lower bounds
are handled separately. Condition (d) is the neighborhood
formulation: $x_n \in V_\varepsilon(L)$ is identical to conditions
(b) and (c) but frames convergence as set membership, which is the
natural language for the topological generalization. The index $K$
plays the same role as $N$ in the base definition
\hyperref[def:convergent-sequence]{Definition~\ref*{def:convergent-sequence}};
the letter changes here to signal that $K$ is the tail offset in
the sense of \hyperref[def:m-tail]{Definition~\ref*{def:m-tail}}.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:convergent-sequence]{Convergence of a Sequence}
  \item \hyperref[def:convergent-sequence-neighborhood]{Convergence --- Neighborhood Formulation}
\end{itemize}
\end{dependencies}





















