\begin{proposition}[Suprema Depend on the Ambient Set]
\label{prop:suprema-ambient-set}
Let $A\subseteq S\subseteq S'$ be subsets of an ordered set. The supremum of $A$ relative to $S$, if it exists, need not agree with the supremum of $A$ relative to $S'$.
\hyperref[prf:suprema-ambient-set]{Go to proof.}
\end{proposition}
\end{propositionbox}

\begin{remark*}[Standard quantified statement]
\[
\sup_S A\text{ and }\sup_{S'} A
\]
are ambient-relative objects and may differ in existence or value.
\end{remark*}

\begin{remark*}[Predicate reading]
\[
\begin{aligned}
&T=S',\qquad A\subseteq S,\qquad S\subseteq T,\\
&P_S=\mathsf{OrderedSet}(S,\leq),\qquad
P_T=\mathsf{OrderedSet}(T,\leq),\\
&\operatorname{LeastUpperBound}(s,A,P_S)
\quad\text{and}\quad
\operatorname{LeastUpperBound}(s,A,P_T)
\end{aligned}
\]
are different assertions unless the ambient upper-bound sets agree.
\end{remark*}

\begin{remark*}[Negated quantified statement]
\[
\sup_S A=\sup_{S'} A
\]
is not guaranteed by $A\subseteq S\subseteq S'$ alone.
\end{remark*}

\begin{remark*}[Negation predicate reading]
\[
\begin{aligned}
&T=S',\qquad A\subseteq S,\qquad S\subseteq T,\\
&P_S=\mathsf{OrderedSet}(S,\leq),\qquad
P_T=\mathsf{OrderedSet}(T,\leq),\\
&\operatorname{LeastUpperBound}(s,A,P_T)\land
\neg\operatorname{LeastUpperBound}(s,A,P_S)
\end{aligned}
\]
is possible when the larger ambient set contains the least upper bound but the smaller one does not.
\end{remark*}

\begin{remark*}[Failure modes]
\begin{description}
  \item[Exposition.]
The ambient-relative supremum can fail to transfer because the candidate least upper bound may not belong to the smaller ambient set, or because the smaller ambient set may have a different collection of upper bounds.


  \item[\operatorname{LeastUpperBound}.]
  \[
\sup_S A=\sup_{S'} A
\]
\[
\begin{aligned}
&T=S',\qquad A\subseteq S,\qquad S\subseteq T,\\
&P_S=\mathsf{OrderedSet}(S,\leq),\qquad
P_T=\mathsf{OrderedSet}(T,\leq),\\
&\operatorname{LeastUpperBound}(s,A,P_T)\land
\neg\operatorname{LeastUpperBound}(s,A,P_S)
\end{aligned}
\]
\end{description}
\end{remark*}

\begin{remark*}[Failure modes]
\begin{description}
  \item[Exposition.]
\[
s=\sup_{S'} A,\quad s\notin S
\Longrightarrow
s\text{ cannot be the supremum of }A\text{ relative to }S.
\]


  \item[\operatorname{LeastUpperBound}.]
  \[
\sup_S A=\sup_{S'} A
\]
\[
\begin{aligned}
&T=S',\qquad A\subseteq S,\qquad S\subseteq T,\\
&P_S=\mathsf{OrderedSet}(S,\leq),\qquad
P_T=\mathsf{OrderedSet}(T,\leq),\\
&\operatorname{LeastUpperBound}(s,A,P_T)\land
\neg\operatorname{LeastUpperBound}(s,A,P_S)
\end{aligned}
\]
\end{description}
\end{remark*}

\begin{remark*}[Interpretation]
Suprema are least upper bounds inside a chosen universe. Enlarging or shrinking that universe can create or remove the point that should serve as the least ceiling.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:ordered-set]{Ordered Set}
  \item \hyperref[def:subset]{Subset}
  \item \hyperref[def:real-upper-bound]{Upper Bound}
  \item \hyperref[def:supremum]{Supremum}
  \item \hyperref[prop:upper-bounds-ambient-order]{Upper Bounds Depend on the Ambient Order}
\end{itemize}
\end{dependencies}


