\newpage
\phantomsection
\label{prf:continuous-hk-integrable}
\LRAProofFor{thm:continuous-hk-integrable}
\begin{remark*}[Return]\hyperref[thm:continuous-hk-integrable]{Return to Theorem}\end{remark*}
\begin{theorem*}[Continuous Functions Are Henstock--Kurzweil Integrable]
Every continuous function \(f:[a,b]\to\mathbb{R}\) is Henstock--Kurzweil
integrable.
\end{theorem*}
\begin{proof}[Professional Standard Proof]
\LRAProofBodyStart
A continuous function on a compact interval is Cauchy-integrable. Cauchy's tag
independence theorem identifies the same value for all sufficiently fine tagged
sums. Thus the function is Riemann-integrable. By the inclusion theorem, every
Riemann-integrable function is Henstock--Kurzweil integrable with the same
value.
\end{proof}
\begin{proof}[Detailed Learning Proof]
\LRAProofBodyStart
Continuity gives enough uniform control for the ordinary Riemann integral.
Once the Riemann integral exists, the gauge definition does not create a new
obstruction: a constant gauge reproduces the Riemann mesh condition. Thus every
continuous function enters the Henstock--Kurzweil class automatically.
\end{proof}
\begin{remark*}[Proof structure]
Use the existing continuous-implies-Riemann theorem, then pass through the
Riemann-to-Henstock--Kurzweil inclusion.
\end{remark*}
\begin{dependencies}
\begin{itemize}
  \item \hyperref[thm:continuous-cauchy-integrable]{Continuous Functions Are Cauchy-Integrable}.
  \item \hyperref[thm:cauchy-tag-independence]{Tag Independence for Continuous Functions}.
  \item \hyperref[thm:riemann-integrable-implies-hk-integrable]{Riemann Integrable Implies Henstock--Kurzweil Integrable}.
\end{itemize}
\end{dependencies}
\clearpage
