\newpage
\phantomsection
\label{prf:c11-placement}
\LRAProofFor{thm:c11-placement}

\begin{remark*}[Return]
\hyperref[thm:c11-placement]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Placement of \(C^{1,1}\)]
For every nondegenerate interval \(I\),
\[
  C^{1,1}(I)\subsetneq C^1(I),
\]
and \(C^{1,1}(I)\) is not contained in \(C^2(I)\). If \(K\) is a compact
interval, then
\[
  C^2(K)\subseteq C^{1,1}(K)\subsetneq C^1(K),
\]
and the first inclusion is strict.
\end{theorem*}

\begin{proof}[Professional Standard Proof]
\LRAProofBodyStart
The inclusion \(C^{1,1}(I)\subseteq C^1(I)\) is part of the definition of
\(C^{1,1}\). It is strict because \(f(x)=|x|^{4/3}\) is \(C^1\) on any
interval containing \(0\), with
\[
  f'(x)=\frac{4}{3}|x|^{1/3}\operatorname{sign}(x),\qquad f'(0)=0,
\]
but
\[
  \frac{|f'(x)-f'(0)|}{|x|}
  =
  \frac{4}{3}|x|^{-2/3}\to\infty
\]
as \(x\to0\). Thus \(f'\) is not Lipschitz near \(0\).

The function \(g(x)=x|x|\) has \(g'(x)=2|x|\), which is Lipschitz with
constant \(2\), so \(g\in C^{1,1}\). But \(g''(0)\) does not exist, since
the derivative of \(2|x|\) has one-sided values \(-2\) and \(2\). Hence
\(C^{1,1}\) is not contained in \(C^2\).

Finally, if \(K\) is compact and \(f\in C^2(K)\), then \(f''\) is continuous
on \(K\), hence bounded by some \(M\). Applying the derivative-bound
corollary to \(f'\) gives \(|f'(x)-f'(y)|\leq M|x-y|\) on \(K\), so
\(f\in C^{1,1}(K)\). The same \(g(x)=x|x|\), restricted to any compact
interval containing \(0\), shows the inclusion \(C^2(K)\subseteq C^{1,1}(K)\)
is strict.
\end{proof}

\begin{proof}[Detailed Learning Proof]
\LRAProofBodyStart
The definition of \(C^{1,1}\) has two requirements: \(f\in C^1\), and the
first derivative is Lipschitz. Forgetting the second requirement immediately
places every \(C^{1,1}\) function in \(C^1\).

The two witness functions show why the new class is a real intermediate
tier. The function \(|x|^{4/3}\) has a continuous first derivative, so it is
\(C^1\), but that derivative becomes too steep near \(0\) to have a finite
Lipschitz constant. The function \(x|x|\) goes the other way: its derivative
is \(2|x|\), which changes at a bounded rate, but \(2|x|\) still has a
corner at \(0\), so no classical second derivative exists there.

On compact intervals, a \(C^2\) function has bounded \(f''\) by the extreme
value theorem. A bounded derivative gives a Lipschitz estimate by the mean
value theorem, so \(f'\) is Lipschitz and \(f\in C^{1,1}\).
\end{proof}

\begin{remark*}[Proof structure]
Use the definition for the easy inclusion, explicit witnesses for strictness,
and the boundedness of \(f''\) on compact intervals for the compact
\(C^2\)-to-\(C^{1,1}\) inclusion.
\end{remark*}

\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:class-c11]{Definition: Lipschitz-Derivative Class \(C^{1,1}\)}
  \item \hyperref[cor:derivative-bound-implies-lipschitz]{Corollary: Derivative Bound Implies Lipschitz}
  \item \hyperref[thm:extreme-value-theorem]{Theorem: Extreme Value Theorem}
\end{itemize}
\end{dependencies}

\clearpage
