\newpage
\phantomsection
\label{prf:archimedean-reciprocal}

\begin{remark*}[Return]
\hyperref[cor:archimedean-reciprocal]{Return to Corollary}
\end{remark*}

\begin{theorem*}[Archimedean Corollary]
For every $\varepsilon \in \mathbb{R}$ such that $\varepsilon > 0$, there exists $n \in \mathbb{N}$ such that $\frac{1}{n} < \varepsilon$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $\varepsilon > 0$. Since $\varepsilon \in \mathbb{R}$, its reciprocal $\frac{1}{\varepsilon}$ is also a real number. By the Archimedean Property, there exists $n \in \mathbb{N}$ such that $n > \frac{1}{\varepsilon}$. Since $n$ and $\varepsilon$ are both positive, we can invert the inequality to obtain $\frac{1}{n} < \varepsilon$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1. Identify the target value for the Archimedean Property.}
We are given a fixed $\varepsilon > 0$. We want to find a natural number $n$ that makes $\frac{1}{n}$ very small. 

\textbf{Step 2. Transform the inequality.}
The goal is $\frac{1}{n} < \varepsilon$. Since $n > 0$ and $\varepsilon > 0$, this is algebraically equivalent to:
\[ n > \frac{1}{\varepsilon} \]
Let $x = \frac{1}{\varepsilon}$. Since $\varepsilon$ is a real number, $x$ is also a real number.

\textbf{Step 3. Apply the Archimedean Property.}
The Archimedean Property states that for any real number $x$, there exists a natural number $n$ such that $n > x$. Applying this to our $x = \frac{1}{\varepsilon}$:
\[ \exists n \in \mathbb{N} : n > \frac{1}{\varepsilon} \]

\textbf{Step 4. Revert to the reciprocal form.}
Starting with $n > \frac{1}{\varepsilon}$, we multiply both sides by $\frac{\varepsilon}{n}$ (which is positive, so the inequality direction is preserved):
\[ \varepsilon > \frac{1}{n} \quad \text{or} \quad \frac{1}{n} < \varepsilon \]
Thus, for any positive tolerance $\varepsilon$, we have found a unit fraction $1/n$ that falls within that tolerance.
\end{proof}

\begin{remark*}[Strategy: The Choice of Leastness Method]
Because this corollary is a direct algebraic consequence of the Archimedean Property, we prove it through simple variable transformation ($x = 1/\varepsilon$) rather than using the supremum's $\varepsilon$-characterization directly. In the hierarchy of your repository, the Archimedean Property (which relies on "leastness") does the heavy lifting, allowing the corollary to be a "Side A" algebraic derivation.
\end{remark*}

\begin{remark*}[Proof structure]
This is a direct proof utilizing the Archimedean Property of $\mathbb{R}$.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[thm:archimedean-property]{Archimedean Property}
  \item \hyperref[ax:field-order-properties]{Order Properties of a Field}
\end{itemize}
\end{remark*}