\newpage
\phantomsection
\label{prf:upper-bound-property-of-supremum}

\begin{remark*}[Return]
\hyperref[prop:upper-bound-property-of-supremum]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Upper Bound Property of Supremum]
Let $A \subseteq \mathbb{R}$ and let $s \in \mathbb{R}$. If $s=\sup A$, then
\[
x \le s
\qquad \text{for every } x \in A.
\]
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Assume that $s=\sup A$. By the definition of supremum, $s$ is an upper bound of $A$. Therefore
\[
\forall x \in A \; (x \le s).
\]
Hence $x \le s$ for every $x \in A$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Fix the set and the candidate supremum.

Let $A \subseteq \mathbb{R}$ and let $s \in \mathbb{R}$. Assume that
\[
s=\sup A.
\]

The goal is to prove that every element of $A$ lies below or at $s$.

\textbf{Step 2.} Recall the first part of the definition of supremum.

By definition, a supremum of a set is in particular an upper bound of that set. Thus from
\[
s=\sup A
\]
it follows that $s$ is an upper bound of $A$.

\textbf{Step 3.} Unpack what “upper bound” means.

To say that $s$ is an upper bound of $A$ means exactly that
\[
\forall x \in A \; (x \le s).
\]

This is already the desired conclusion.

\textbf{Step 4.} State the result in ordinary mathematical language.

Since
\[
\forall x \in A \; (x \le s),
\]
it follows that
\[
x \le s
\qquad \text{for every } x \in A.
\]

Therefore every element of $A$ lies below the supremum.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct unpacking proof. The proposition isolates the upper-bound part of the definition of supremum, so the argument consists of invoking the definition and then rewriting the conclusion in ordinary quantified form.
\end{remark*}

\begin{remark*}[Dependencies]\hfill
\begin{itemize}
  \item \hyperref[def:supremum]{Definition of Supremum}
  \item \hyperref[def:upper-bound]{Definition of Upper Bound}
\end{itemize}
\end{remark*}