\newpage
\phantomsection
\label{prf:supremum-in-the-set-is-the-maximum}

\begin{remark*}[Return]
\hyperref[prop:supremum-in-the-set-is-the-maximum]{Return to Proposition}
\end{remark*}

\begin{theorem*}[Supremum in the Set Is the Maximum]
Let $s = \sup A$. If $s \in A$, then $s$ is the maximum of $A$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $A \subseteq \mathbb{R}$ be a non-empty set bounded above, and let $s = \sup A$. By the definition of the supremum, $s$ is an upper bound of $A$, which implies $s \ge a$ for all $a \in A$. 

The definition of a maximum $m$ of a set $A$ requires two conditions:
1. $m \in A$
2. $m \ge a$ for all $a \in A$

We are given the hypothesis that $s \in A$, satisfying the first condition. From the definition of supremum, we have $s \ge a$ for all $a \in A$, satisfying the second condition. Therefore, $s$ satisfies the definition of the maximum of $A$. Since the maximum is unique, we conclude that $s = \max A$.
\end{proof}

\begin{remark*}[Detailed Learning Proof]~\\
\textbf{Step 1.} Identify the "Guard" property of the supremum. By definition, $s = \sup A$ is an upper bound, meaning it stands as a ceiling for all elements in $A$, so $s \ge a$ for all $a \in A$.

\textbf{Step 2.} State the dual requirements for a maximum. To be a maximum, a value must be both an element of the set ($m \in A$) and an upper bound of the set ($\forall a \in A, m \ge a$).

\textbf{Step 3.} Synthesize the available information. The hypothesis provides $s \in A$, and the property of the supremum provides the upper bound condition $s \ge a$.

\textbf{Step 4.} Apply the definition of maximum. Because $s$ meets both required criteria, it is the maximum. The uniqueness of the maximum ensures this identity is absolute.
\end{remark*}

\begin{remark*}[Interpretation]
This proof demonstrates the relationship between the "frontier" of a set and its members. While a supremum is the tightest possible guard (the Control), it does not usually have to be part of the set (e.g., $(0, 1)$ has supremum $1 \notin (0,1)$). However, if that guard actually sits on a member of the set ($s \in A$), it becomes the "tallest" member, thereby satisfying the definition of a maximum.
\end{remark*}