\newpage
\phantomsection
\label{prf:riemann-mcshane-hk-inclusions}
\LRAProofFor{thm:riemann-mcshane-hk-inclusions}
\begin{remark*}[Return]\hyperref[thm:riemann-mcshane-hk-inclusions]{Return to Theorem}\end{remark*}
\begin{theorem*}[Riemann Integrable Implies McShane Integrable Implies Henstock--Kurzweil Integrable]
On a compact interval,
\[
  \mathcal R[a,b]\subseteq \mathcal M[a,b]\subseteq \mathcal{HK}[a,b],
\]
with agreement of integral values.
\end{theorem*}
\begin{proof}[Professional Standard Proof]
\LRAProofBodyStart
First suppose \(f\) is McShane integrable with value \(A\). Every
Henstock--Kurzweil \(\delta\)-fine tagged partition is McShane
\(\delta\)-fine, because HK adds the extra restriction that each tag lies in
its own interval. Hence the McShane estimate applies to all HK partitions, so
\(f\) is HK-integrable with the same value.

Now suppose \(f\) is Riemann integrable with value \(L\). By the Lebesgue
criterion, its discontinuity set has measure zero. Let \(M\) bound \(|f|\).
Choose an open cover \(G\) of the discontinuity set with total length so small
that \(2M|G|<\varepsilon/3\). Define the gauge at discontinuity points so that
their gauge balls lie inside \(G\). At each continuity point \(x\), choose the
gauge so small that \(|f(y)-f(x)|\) is small whenever \(y\) lies in the gauge
ball.

For any McShane-fine partition, split the intervals according to whether
their tags are discontinuity points or continuity points. The first class has
total length controlled by \(|G|\), hence contributes less than
\(\varepsilon/3\). On the second class, the free tag may sit outside its
interval, but the entire interval lies inside the tag's continuity ball, so
the oscillation error is small. Comparing these sums with ordinary Darboux
sums for \(f\) and using the Riemann value \(L\) gives
\[
  |S(f,P,\xi)-L|<\varepsilon.
\]
Thus \(f\) is McShane integrable and the value is \(L\).
\end{proof}
\begin{proof}[Detailed Learning Proof]
\LRAProofBodyStart
The inclusion \(\mathcal M\subseteq\mathcal{HK}\) is a quantifier argument:
McShane tests more partitions. If a function survives every McShane-fine
partition, it automatically survives the smaller family of HK-fine partitions.

The inclusion \(\mathcal R\subseteq\mathcal M\) is the same philosophy as the
Lebesgue criterion. Riemann integrability says the bad points are null. Around
those points the gauge is made so small that all intervals tagged there occupy
negligible total length. Away from those points the function is continuous, so
a tag controls every nearby point in the interval it authorizes. Free tags do
not break the argument because the McShane condition still forces the whole
interval to lie inside the tag's gauge ball.
\end{proof}
\begin{remark*}[Proof structure]
Use the inclusion of partition classes for McShane \(\Rightarrow\) HK, and use
the null discontinuity set plus local continuity gauges for
Riemann \(\Rightarrow\) McShane.
\end{remark*}
\begin{remark*}[Forward dependency]
This proof uses the Lebesgue criterion proved in the next proof topic. The
chapter order presents McShane before measure zero for conceptual flow, but
the dependency graph points forward to the criterion.
\end{remark*}
\begin{dependencies}
\begin{itemize}
  \item \hyperref[def:mcshane-fine-tagged-partition]{McShane-Fine Tagged Partition}.
  \item \hyperref[def:mcshane-integral]{McShane Integral}.
  \item \hyperref[def:henstock-kurzweil-integral]{Henstock--Kurzweil Integral}.
  \item \hyperref[thm:lebesgue-criterion-riemann-integrability]{Lebesgue Criterion for Riemann Integrability}.
\end{itemize}
\end{dependencies}
\clearpage
