\newpage
\phantomsection
\label{prf:uniqueness-of-derivative}

\begin{remark*}[Return]
\hyperref[thm:uniqueness-of-the-derivative]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Uniqueness of the Derivative]
Let $I \subseteq \mathbb{R}$ be an open interval, let $f : I \to \mathbb{R}$, and let $c \in I$. If $f$ is differentiable at $c$, then $f'(c)$ is unique.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Suppose both $L_1$ and $L_2$ satisfy the definition of the derivative at $c$. Then both are values of the limit $\lim_{x \to c} \frac{f(x)-f(c)}{x-c}$. By the Uniqueness of Limits of Functions, this limit has at most one value. Therefore $L_1 = L_2$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Suppose both $L_1$ and $L_2$ satisfy the definition of the derivative at $c$. By definition of the derivative, this means both $L_1$ and $L_2$ equal $\lim_{x \to c} \frac{f(x)-f(c)}{x-c}$. The difference quotient $\frac{f(x)-f(c)}{x-c}$ is a function of $x$ defined for all $x \in I$ with $x \neq c$.

\textbf{Step 2.} Since $I$ is an open interval and $c \in I$, the point $c$ is a cluster point of the domain $I \setminus \{c\}$. The Uniqueness of Limits of Functions theorem states that if a function has a limit at a cluster point, then that limit is unique.

\textbf{Step 3.} Therefore, the limit $\lim_{x \to c} \frac{f(x)-f(c)}{x-c}$ can have at most one value. Since both $L_1$ and $L_2$ equal this limit, it follows that $L_1 = L_2$.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof by reduction to a previously established result. The strategy is to recognize that the derivative is defined as a limit of the difference quotient, then apply the general theorem that limits are unique. The proof works because it reduces a specific question about derivatives to the general principle of uniqueness of limits.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:derivative]{Definition of Derivative}
  \item \hyperref[thm:limit-unique]{Uniqueness of Limits of Functions}
\end{itemize}
\end{remark*}
