\newpage
\phantomsection
\label{prf:derivative-inverse-function-on-interval}

\begin{remark*}[Return]
\hyperref[thm:inverse-function-theorem-global]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Inverse Function Theorem — Global Form]
Let $I \subseteq \mathbb{R}$ be an interval, and let $f : I \to \mathbb{R}$ be strictly monotone and differentiable on $I$ with $f'(x) \neq 0$ for all $x \in I$. Set $J := f(I)$ and let $g : J \to \mathbb{R}$ be the inverse of $f$. Then $g$ is differentiable on $J$ and $g' = 1/(f' \circ g)$ on $J$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $d \in J$ be arbitrary. Since $g$ is the inverse of $f$, there exists a unique $c \in I$ with $f(c) = d$, namely $c = g(d)$. By hypothesis $f$ is differentiable at $c$ with $f'(c) \neq 0$, so by the pointwise Inverse Function Theorem, $g$ is differentiable at $d$ and $g'(d) = 1/f'(c) = 1/f'(g(d)) = 1/(f' \circ g)(d)$. Since $d \in J$ was arbitrary, $g$ is differentiable on $J$ and $g' = 1/(f' \circ g)$ on $J$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Let $d \in J$ be arbitrary and establish the correspondence with the domain. Since $g$ is the inverse of $f$, there exists a unique $c \in I$ such that $f(c) = d$, namely $c = g(d)$. This establishes the bijective correspondence between points in the range $J$ and points in the domain $I$.

\textbf{Step 2.} Apply the pointwise theorem at the corresponding domain point. By hypothesis, $f$ is differentiable at $c$ with $f'(c) \neq 0$. The pointwise Inverse Function Theorem therefore applies at $c$, guaranteeing that $g$ is differentiable at $d$ with derivative $g'(d) = 1/f'(c)$.

\textbf{Step 3.} Express the derivative in terms of the composition. Substituting $c = g(d)$ into the derivative formula yields $g'(d) = 1/f'(g(d)) = 1/(f' \circ g)(d)$. This expresses the derivative of the inverse function in terms of the composition of the original derivative with the inverse function.

\textbf{Step 4.} Conclude by universality. Since $d \in J$ was arbitrary, the differentiability and derivative formula hold at every point of $J$. Therefore $g$ is differentiable on $J$ and $g' = 1/(f' \circ g)$ on $J$.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof using universal instantiation. The global statement is established by taking an arbitrary point in the range and applying the pointwise Inverse Function Theorem at the corresponding domain point. The key insight is that the bijective nature of the inverse function allows the pointwise result to be lifted to a global statement through the arbitrariness of the range point.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[thm:inverse-function-theorem-monotone]{Inverse Function Theorem (Monotone Version)}
\end{itemize}
\end{remark*}