\newpage
\phantomsection
\label{prf:derivative-h-form-equivalence}

\begin{remark*}[Return]
\hyperref[prop:derivative-h-form-equivalence]{Return to Proposition}
\end{remark*}

\begin{theorem*}[Derivative: $h$-Form Equivalence]
Let $I \subseteq \mathbb{R}$ be an open interval, let $f : I \to \mathbb{R}$, and let $c \in I$. The following are equivalent:
\begin{enumerate}
\item $f$ is differentiable at $c$.
\item The limit $\displaystyle\lim_{h \to 0} \frac{f(c + h) - f(c)}{h}$ exists.
\end{enumerate}
In this case, $\displaystyle f'(c) = \lim_{h \to 0} \frac{f(c + h) - f(c)}{h}$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
The substitution $h = x - c$ is a bijection from $\{x \in I : x \neq c\}$ to $\{h \in \mathbb{R} : h \neq 0, c+h \in I\}$. Under this substitution, $x \to c$ if and only if $h \to 0$, and $\frac{f(x)-f(c)}{x-c} = \frac{f(c+h)-f(c)}{h}$ identically. Therefore the two limits exist simultaneously and are equal when either exists.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Identify the substitution relating the two forms. Set $h = x - c$, equivalently $x = c + h$. For $x \in I$ with $x \neq c$, this gives $h \neq 0$ and $c + h \in I$. The substitution is bijective: every admissible $x$ corresponds to a unique admissible $h$ and vice versa.

\textbf{Step 2.} Verify the difference quotients are identical under the substitution. For any such $x$ and $h$:
\[
\frac{f(x) - f(c)}{x - c} = \frac{f(c + h) - f(c)}{h}.
\]
This is a pure algebraic identity requiring no limits.

\textbf{Step 3.} Verify the limit variable transforms correctly. As $x \to c$ through $I \setminus \{c\}$, $h = x - c \to 0$; conversely as $h \to 0$ with $c + h \in I$, $x = c + h \to c$. The correspondence between the limit processes is exact.

\textbf{Step 4.} Conclude the equivalence. Since the same function of the same variable is approached through the same deleted neighbourhood, the two limits exist simultaneously and agree:
\[
\lim_{x \to c} \frac{f(x)-f(c)}{x-c} = L
\;\iff\;
\lim_{h \to 0} \frac{f(c+h)-f(c)}{h} = L.
\]
Hence $f$ is differentiable at $c$ (in the $x$-form sense) if and only if the $h$-form limit exists, and both equal $f'(c)$ when they do.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct equivalence proof by change of variables. The substitution $h = x - c$ is a translation that converts one parameterisation of the punctured neighbourhood of $c$ into another. Because the substitution is bijective and the difference quotients are identical under it, the two limit definitions are literally the same limit under different notation. No $\varepsilon$-$\delta$ argument is needed beyond the observation that the substitution preserves the limit process.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:derivative-at-a-point]{Definition: Derivative at a Point}
\end{itemize}
\end{remark*}
