\newpage
\phantomsection
\label{prf:sum-rule}

\begin{remark*}[Return]
\hyperref[thm:sum-rule]{Return to Theorem}
\end{remark*}

\begin{theorem*}[Sum Rule]
Let $I \subseteq \mathbb{R}$ be an open interval, let $c \in I$, and let $f, g : I \to \mathbb{R}$ be differentiable at $c$. Then $f + g$ is differentiable at $c$ and $(f + g)'(c) = f'(c) + g'(c)$.
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
Let $h := f + g$. For $x \in I$ with $x \neq c$, the difference quotient expands as
\[
  \frac{h(x) - h(c)}{x - c} = \frac{(f(x) + g(x)) - (f(c) + g(c))}{x - c} = \frac{f(x) - f(c)}{x - c} + \frac{g(x) - g(c)}{x - c}.
\]
By the Sum Rule for Limits,
\[
  \lim_{x \to c} \frac{h(x) - h(c)}{x - c} = \lim_{x \to c} \frac{f(x) - f(c)}{x - c} + \lim_{x \to c} \frac{g(x) - g(c)}{x - c} = f'(c) + g'(c),
\]
where the individual limits exist and equal $f'(c)$ and $g'(c)$ by differentiability of $f$ and $g$ at $c$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Form and split the difference quotient of $h := f + g$. For $x \in I$ with $x \neq c$, substituting $h(x) = f(x) + g(x)$ and grouping terms gives
\[
  \frac{h(x) - h(c)}{x - c} = \frac{(f(x) + g(x)) - (f(c) + g(c))}{x - c} = \frac{f(x) - f(c)}{x - c} + \frac{g(x) - g(c)}{x - c}.
\]
This step relies purely on arithmetic of real numbers and the linearity of addition.

\textbf{Step 2.} Pass to the limit using the Sum Rule for Limits. Since both $f$ and $g$ are differentiable at $c$, the limits $\lim_{x \to c} \frac{f(x) - f(c)}{x - c}$ and $\lim_{x \to c} \frac{g(x) - g(c)}{x - c}$ exist and equal $f'(c)$ and $g'(c)$ respectively. By the Sum Rule for Limits,
\[
  \lim_{x \to c} \frac{h(x) - h(c)}{x - c} = \lim_{x \to c} \frac{f(x) - f(c)}{x - c} + \lim_{x \to c} \frac{g(x) - g(c)}{x - c} = f'(c) + g'(c).
\]
Therefore $h$ is differentiable at $c$ and $h'(c) = f'(c) + g'(c)$.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof using algebraic manipulation and limit properties. The difference quotient of $f + g$ splits linearly into the sum of the individual difference quotients by arithmetic. The Sum Rule for Limits then distributes the limit across the sum, and differentiability of $f$ and $g$ supplies the two derivative values.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:derivative-at-point]{Definition of Differentiability at a Point}
  \item \hyperref[thm:limit-sum]{Sum Rule for Limits}
\end{itemize}
\end{remark*}