\newpage
\phantomsection
\label{prf:increment-definition-derivative}

\begin{remark*}[Return]
\hyperref[prop:derivative-h-form-equivalence]{Return to Proposition}
\end{remark*}

\begin{theorem*}[Equivalence of Derivative Definitions]
A function $f: (a,b) \to \mathbb{R}$ is differentiable at $c \in (a,b)$ if and only if 
\[ \lim_{h \to 0} \frac{f(c+h) - f(c)}{h} = f'(c). \]
\end{theorem*}

\begin{proof}
\textbf{Professional Standard Proof.}~\\
$(\Rightarrow)$ Assume $f$ is differentiable at $c$, so $\lim_{x \to c} \frac{f(x) - f(c)}{x - c} = f'(c)$. Substituting $h = x - c$ gives $x = c + h$, and as $x \to c$, we have $h \to 0$. Therefore $\lim_{h \to 0} \frac{f(c+h) - f(c)}{h} = \lim_{x \to c} \frac{f(x) - f(c)}{x - c} = f'(c)$.

$(\Leftarrow)$ Conversely, assume $\lim_{h \to 0} \frac{f(c+h) - f(c)}{h} = f'(c)$. Setting $x = c + h$ gives $h = x - c$, and as $h \to 0$, we have $x \to c$. Thus $\lim_{x \to c} \frac{f(x) - f(c)}{x - c} = \lim_{h \to 0} \frac{f(c+h) - f(c)}{h} = f'(c)$, establishing differentiability at $c$.
\end{proof}

\begin{proof}
\textbf{Detailed Learning Proof.}~\\

\textbf{Step 1.} Establish the forward direction by variable substitution. Assume $f$ is differentiable at $c$, meaning $\lim_{x \to c} \frac{f(x) - f(c)}{x - c} = f'(c)$ exists. The substitution $h = x - c$ transforms this limit: when $x = c + h$, the condition $x \to c$ becomes $h \to 0$ since $(c + h) \to c$ precisely when $h \to 0$.

\textbf{Step 2.} Apply the substitution to transform the limit expression. Under the substitution $h = x - c$, the difference quotient becomes $\frac{f(x) - f(c)}{x - c} = \frac{f(c + h) - f(c)}{h}$. The limit transformation preserves the value: $\lim_{x \to c} \frac{f(x) - f(c)}{x - c} = \lim_{h \to 0} \frac{f(c + h) - f(c)}{h}$.

\textbf{Step 3.} Establish the reverse direction using the inverse substitution. Assume $\lim_{h \to 0} \frac{f(c+h) - f(c)}{h} = f'(c)$ exists. The reverse substitution $x = c + h$ (equivalently $h = x - c$) transforms this limit back to the standard form.

\textbf{Step 4.} Complete the bidirectional equivalence. Under the reverse substitution, $h \to 0$ becomes $x \to c$, and the expression $\frac{f(c+h) - f(c)}{h}$ becomes $\frac{f(x) - f(c)}{x - c}$. Therefore $\lim_{h \to 0} \frac{f(c+h) - f(c)}{h} = \lim_{x \to c} \frac{f(x) - f(c)}{x - c} = f'(c)$, confirming differentiability at $c$.
\end{proof}

\begin{remark*}[Proof structure]
This is a direct proof establishing logical equivalence through variable substitution. The strategy demonstrates that both derivative definitions are merely different parameterizations of the same geometric concept: the slope of the secant line approaching the tangent line. The bijective nature of the linear substitution $h = x - c$ preserves all limit properties, making the equivalence immediate once the correspondence is established.
\end{remark*}

\begin{remark*}[Dependencies]~\\
\begin{itemize}
  \item \hyperref[def:differentiability]{Definition of Differentiability}
  \item \hyperref[def:limit]{Definition of Limit}
  \item \hyperref[thm:limit-substitution]{Limit Substitution Theorem}
\end{itemize}
\end{remark*}