% ==================================================
% Algebra of Summations
% Discrete Calculus
% ==================================================

\section{Algebra of Summations}
\label{sec:summation-algebra}

Having established the difference operator and the telescoping identity,
we now collect the basic algebraic rules for manipulating summations.
These identities allow sums to be combined, split, and reindexed while
preserving their value.

\begin{tcolorbox}[colback=gray!6, colframe=gray!40, arc=2pt,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  title={\small\textbf{Summation Algebra — Quick Reference}},
  fonttitle=\small\bfseries]
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{}ll@{}}
\textbf{Linearity} & $\sum(af+bg) = a\sum f + b\sum g$ \\
\textbf{Splitting} & $\sum_a^c = \sum_a^b + \sum_{b+1}^c$ \\
\textbf{Index shift} & $\sum_{k=a}^{b} f(k) = \sum_{k=a+1}^{b+1} f(k-1)$ \\
\textbf{Constant sum} & $\sum_{k=a}^{b} c = (b-a+1)c$ \\
\textbf{Empty sum} & $\sum_{k=a}^{b} f(k) = 0$ when $a > b$ \\
\textbf{Nested sums} & $\sum_i\sum_j a_{ij} = \sum_j\sum_i a_{ij}$ (independent limits) \\
\end{tabular}
\end{tcolorbox}

\section*{Linearity}

Summation is a linear operator. For functions \(f\) and \(g\) and
constants \(a\) and \(b\),
\[
\sum_{k=m}^{n} (a\,f(k) + b\,g(k))
=
a \sum_{k=m}^{n} f(k)
+
b \sum_{k=m}^{n} g(k).
\]
This allows constants to be factored out of a sum and sums of expressions
to be separated.

\begin{example*}
\(\displaystyle\sum_{k=1}^{n} (2k + 3)
= 2\sum_{k=1}^{n} k + 3\sum_{k=1}^{n} 1.\)
\end{example*}

\section*{Splitting a Sum}

A sum over an interval may be divided into pieces:
\[
\sum_{k=a}^{c} f(k)
=
\sum_{k=a}^{b} f(k)
+
\sum_{k=b+1}^{c} f(k)
\qquad \text{whenever } a \le b < c.
\]

\begin{example*}
\(\displaystyle\sum_{k=1}^{10} f(k)
= \sum_{k=1}^{5} f(k) + \sum_{k=6}^{10} f(k).\)
\end{example*}

\section*{Index Renaming}

The index of summation is a \emph{dummy variable}:
\[
\sum_{k=a}^{b} f(k)
=
\sum_{i=a}^{b} f(i).
\]
This is useful when manipulating expressions containing several sums,
since the index variable can be renamed to avoid conflicts.

\section*{Index Shifting}

It is often convenient to shift the summation index:
\[
\sum_{k=a}^{b} f(k)
=
\sum_{k=a+1}^{b+1} f(k-1).
\]
Index shifting allows sums to be aligned so that terms cancel or
combine properly. It appears frequently in proofs involving
recurrence relations and discrete calculus identities.

\begin{example*}
\(\displaystyle\sum_{k=0}^{n} f(k+1) = \sum_{k=1}^{n+1} f(k).\)
\end{example*}

\section*{Constant Sum}

If the summand does not depend on the index, the sum counts terms:
\[
\sum_{k=a}^{b} c = (b-a+1)\,c.
\]
The quantity \(b-a+1\) is the number of integers between \(a\) and \(b\),
inclusive.

\begin{example*}
\(\displaystyle\sum_{k=3}^{7} 5 = 5 \cdot 5 = 25.\)
\end{example*}

\section*{Empty Sum}

If the upper limit is smaller than the lower limit, the sum contains no
terms. By convention,
\[
\sum_{k=a}^{b} f(k) = 0 \qquad \text{whenever } a>b.
\]
This convention simplifies many algebraic identities and allows formulas
to remain valid without special cases.

\section*{Nested Sums}

Summations may be nested:
\[
\sum_{i=1}^{n}\sum_{j=1}^{m} a_{ij}
= \sum_{i=1}^{n} \Bigl(a_{i1}+a_{i2}+\cdots+a_{im}\Bigr).
\]
When the limits are independent, the order may be exchanged:
\[
\sum_{i=1}^{n}\sum_{j=1}^{m} a_{ij}
=
\sum_{j=1}^{m}\sum_{i=1}^{n} a_{ij}.
\]

\begin{remark*}[Analogy with double integrals]
Exchanging summation order is the discrete analogue of Fubini's theorem
for iterated integrals.
\end{remark*}

\subsection{Common Summation Identities}
\label{sec:common-summation-identities}

Many sums that appear in discrete mathematics and discrete calculus have
closed-form expressions. The following identities are among the most
frequently encountered.

\begin{tcolorbox}[colback=gray!6, colframe=gray!40, arc=2pt,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  title={\small\textbf{Common Summation Identities}},
  fonttitle=\small\bfseries]
\renewcommand{\arraystretch}{1.7}
\begin{tabular}{@{}ll@{}}
$\displaystyle\sum_{k=1}^{n} 1 = n$ &
$\displaystyle\sum_{k=1}^{n} k = \dfrac{n(n+1)}{2}$ \\[10pt]
$\displaystyle\sum_{k=1}^{n} k^2 = \dfrac{n(n+1)(2n+1)}{6}$ &
$\displaystyle\sum_{k=1}^{n} k^3 = \left(\dfrac{n(n+1)}{2}\right)^2$ \\[10pt]
$\displaystyle\sum_{k=0}^{n} r^k = \dfrac{1-r^{n+1}}{1-r}\;\;(r\neq 1)$ &
$\displaystyle\sum_{k=0}^{n}\binom{n}{k} = 2^n$
\end{tabular}
\end{tcolorbox}

\begin{remark*}[Role in discrete calculus]
Polynomial summation formulas play an important role when working with
finite differences and Newton series, while geometric sums arise naturally
in recurrence relations and generating functions. Many of these identities
can be derived systematically using the falling factorial basis and
the Fundamental Theorem of Finite Calculus introduced later in this chapter.
\end{remark*}
