% ============================================================
%  Proof Techniques — Notes Entry Point
%  Volume III · Real Analysis
%  volume-iii/analysis/real-analysis/notes/proof-techniques/index.tex
% ============================================================

% ── Breadcrumb ───────────────────────────────────────────────
\begin{tcolorbox}[
  colback=gray!6, colframe=gray!40, arc=2pt,
  left=8pt, right=8pt, top=6pt, bottom=6pt,
  title={\small\textbf{Where You Are in the Journey}},
  fonttitle=\small\bfseries
]
\begin{center}
\small
Real Numbers $\;\to\;$ Sequences $\;\to\;$
\textbf{Proof Techniques} $\;\to\;$
Limits and Convergence $\;\to\;$ Continuity $\;\to\;$ $\cdots$
\end{center}

\medskip
\noindent\textbf{How we got here.}
The real numbers are now constructed and their completeness — the Axiom of
Completeness, or equivalently the Nested Interval Property and the Monotone
Convergence Theorem — is established. Sequences have been defined and the
basic limit machinery (Algebraic Limit Theorem, Order Limit Theorem) is in
place. The prerequisite for this chapter is fluency with the $\varepsilon$-$N$
definition and with the order axioms of $\mathbb{R}$.

\medskip
\noindent\textbf{What this chapter builds.}
This chapter makes explicit the recurring proof patterns of real analysis: the
inequality arithmetic underlying every $\varepsilon$-$N$ argument; the use of
completeness as a constructive engine for building sequences from sets; the
predicate-walking technique for extracting subsequences; and the bisection and
nested-interval method for locating limit points. These are the four tools that
appear, in various combinations, in nearly every theorem of the subject.

\medskip
\noindent\textbf{Where this leads.}
Every technique catalogued here will be deployed in the chapters that follow.
Inequality bounding drives the convergence and continuity arguments. Inductive
selection is the mechanism behind the Monotone Convergence Theorem and the
$\varepsilon$-characterisation of suprema. Predicate-walking underpins
Bolzano--Weierstrass and Arzel\`a--Ascoli. Bisection and NIP reappear in the
Intermediate Value Theorem, Heine--Borel, and the completeness proofs for
metric spaces. The residue partition technique drives the Alternating Series
Test and recurs in Ces\`aro summation and Fourier analysis.
\end{tcolorbox}
\vspace{1em}

% ── Structural Roadmap ───────────────────────────────────────
\subsection*{Structural Roadmap}

Each section is organised as:
\begin{center}
\textbf{Core tool or definition $\longrightarrow$
Canonical applications $\longrightarrow$
Limitations and forward connections}
\end{center}

The five sections, in dependency order:
\begin{enumerate}
  \item \textbf{Manipulating Inequalities and the Logic of Bounding.}
        The foundational arithmetic of $\leq$: the triangle inequality,
        the $\varepsilon$-budget split, the boundedness replacement, the
        work-backwards principle. No completeness is required; these are
        consequences of the ordered field axioms alone.

  \item \textbf{Completeness as a Constructive Engine.}
        How the $\varepsilon$-characterisation of $\sup$ and $\inf$, together
        with the Archimedean Property, produces monotone sequences converging
        to extremal values. Includes the inductive selection construction and
        the equivalence LUB\,$\Leftrightarrow$\,MCT.

  \item \textbf{Walking a Sequence with a Predicate.}
        The infinitely-often / eventually dichotomy; the abstract extraction
        template; the peak argument (Monotone Subsequence Theorem); the
        bisection-occupancy variant (Bolzano--Weierstrass); the diagonal
        extraction (Arzel\`a--Ascoli). Limitations of the technique.

  \item \textbf{Interval Bisection and Nested Intervals.}
        The Nested Interval Property as a theorem and as a proof engine.
        The bisection sequence; IVT and uncountability as canonical
        applications. Comparison of the NIP and AoC proof paths.

  \item \textbf{Subsequence Partition via Residue Classes.}
        The $k$-periodicity convergence criterion; the even/odd partition
        proof of the Alternating Series Test; the divergence corollary.
        Contrast with predicate-walking and limitations.
\end{enumerate}

\begin{remark}[Primary sources]
Abbott \S1.4, \S2.4, \S2.5; Lebl \S1.3, \S2.1, \S2.3; Tao \S6.3, \S6.4;
Pugh \S\S1--2.
\end{remark}

\medskip

% ── Section inputs (dependency order) ────────────────────────
\input{volume-iii/analysis/real-analysis/notes/proof-techniques/01-inequalities-bounding}
\input{volume-iii/analysis/real-analysis/notes/proof-techniques/02-completeness-construction}
\input{volume-iii/analysis/real-analysis/notes/proof-techniques/03-predicate-walking}
\input{volume-iii/analysis/real-analysis/notes/proof-techniques/04-bisection-nested-intervals}
\input{volume-iii/analysis/real-analysis/notes/proof-techniques/05-residue-partition}
